\documentclass[11pt]{article}

\usepackage[backend=bibtex,natbib,style=numeric-comp,sorting=none,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{refs}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

\newcommand{\Aeff}{\alpha'_{\mathrm{eff}}}
\newcommand{\Sym}{\mathrm{Sym}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\bC}{\mathbb{C}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\gh}{\mathrm{gh}}
\newcommand{\ie}{\begin{equation}\begin{aligned}}
\newcommand{\fe}{\end{aligned}\end{equation}}

\title{A Curved First-Order String for \texorpdfstring{$\Sym^N(\bR^8)$}{SymN(R8)} on a Two-Dimensional Spacetime}
\author{}
\date{}

\begin{document}
\maketitle

\section{Aim}
This note records a concrete conjectural starting point for a string dual of the symmetric-orbifold SCFT
\begin{equation}\label{eq:proposed-dual-cft}
\Sym^N(\bR^8)
\end{equation}
living on a two-dimensional spacetime $C$. More explicitly, this means the $S_N$ orbifold of $N$ copies of the free $(8,8)$ SCFT of eight noncompact bosons and fermions. Here $C$ is itself the target of the longitudinal first-order string variables. The scope of the note is deliberately narrow: it concerns the exact symmetric-orbifold CFT itself, not a deformation of the orbifold action and not the full two-dimensional $(8,8)$ gauge theory away from that point.

The status is mixed. The local worldsheet system is explicit and is just the supersymmetric first-order string already present in the Gomis--Ooguri description of the NCOS/NRCS limit \cite{gomis2000nonrelativisticclosedstringtheory}. Its Poisson/BF core already has the structural feature one wants for a dual of a two-dimensional CFT on $C$: the target metric representative drops out, so only the complex/Weyl structure of $C$ matters. The extension from flat target $C=\bC$ to a general Riemann surface $C$ is also explicit at the level of local patching data. A companion BRST analysis recorded separately in this project shows that, for the full super longitudinal multiplet, the BRST current and BRST charge do patch globally on a target curve. Separate companion notes then derive the exact finite-$N$ external-state normalization for the lowest single-cycle sphere sector and, more generally, for arbitrary NS--NS multi-string profiles $\lambda_i$ on the three tubes. The sewn-cover derivation below then upgrades that NS--NS multi-string normalization into an exact genus-zero amplitude match on $C_{0,3}$. What is \emph{not} yet proved in general is instead the compactified BRST-complete local puncture operator that packages those constituent sewn-cover insertions into one multi-string vertex on a target tube, the extension to Ramond sectors, and the full nonchiral quantum completion of the curved theory. Any attempt to connect this exact proposal to matrix string theory would require deforming the Poisson-sigma model away from this core, and that is not part of the present note.

Throughout, $\Sigma$ denotes the worldsheet Riemann surface, $C$ denotes the two-dimensional target/spacetime, and $\Aeff$ denotes the effective string scale inherited from the non-relativistic string limit. Because the transverse theory is noncompact, any partition function involving the $\bR^8$ seed theory is understood either per unit transverse volume or, equivalently for the free formulas used below, after factoring out the center-of-mass zero modes. Whenever a formula is imported from \cite{gomis2000nonrelativisticclosedstringtheory} or from the curved-$\beta\gamma$ literature \cite{nekrasov2005curvedbetagammasystems}, I will say so explicitly.

\section{Flat-Space Starting Point}
The local matter system is taken as input. Concretely, I start from the critical type-II first-order string built from a longitudinal super-$\beta\gamma$ multiplet together with eight transverse free superfields, namely the local Gomis--Ooguri matter system written in $(1,1)$ superspace. On a Euclidean worldsheet with coordinates $(z,\bar z,\vartheta,\bar\vartheta)$, define
\begin{equation}\label{eq:superderivatives}
D=\partial_\vartheta+\vartheta\,\partial,
\qquad
\bar D=\partial_{\bar\vartheta}+\bar\vartheta\,\bar\partial,
\qquad
D^2=\partial,
\qquad
\bar D^2=\bar\partial.
\end{equation}
The flat-space action is
\begin{equation}\label{eq:flat-action}
\begin{aligned}
S_{\mathrm{flat}}
&=
\frac{1}{2\pi}\int d^2z\,d\vartheta\,d\bar\vartheta\,
\left[
\mathbf B\,\bar D\mathbf X^+
+\bar{\mathbf B}\,D\mathbf X^-
+\frac{1}{4\Aeff}\,D\mathbf X^+\,\bar D\mathbf X^-
\right]
+S_\perp,
\\
S_\perp
&=
\frac{1}{2\pi \Aeff}\int d^2z\,d\vartheta\,d\bar\vartheta\,
\delta_{ij}\,D\mathbf Y^i\,\bar D\mathbf Y^j,
\qquad i=1,\dots,8.
\end{aligned}
\end{equation}
Here $\mathbf X^\pm$ are bosonic longitudinal superfields, $\mathbf B$ and $\bar{\mathbf B}$ are fermionic first-order superfields, and $\mathbf Y^i$ with $i=1,\dots,8$ are transverse free superfields.
In Lorentzian signature one may think of $X^\pm=X^0\pm X^1$. For the curved-target discussion below it is more convenient to view $X^+$ as a local holomorphic coordinate on the target Riemann surface $C$ and $X^-$ as the corresponding antiholomorphic coordinate.

In Euclidean signature the physical contour should impose the reality condition
\begin{equation}\label{eq:euclidean-reality}
X^-=\overline{X^+},
\end{equation}
even though the first-order path integral is most conveniently written in terms of independent fields $\mathbf X^\pm$ before one chooses that contour.

The equations of motion of the flat first-order system give the bulk constraints
\begin{equation}\label{eq:bulk-chiral-constraints}
\bar D\mathbf X^+=0,
\qquad
D\mathbf X^-=0,
\qquad
\bar D\mathbf B=0,
\qquad
D\bar{\mathbf B}=0.
\end{equation}
So on shell the longitudinal superfields are chiral,
\begin{equation}\label{eq:onshell-plus}
\mathbf X^+(z,\vartheta)=\gamma(z)+\vartheta\,c(z),
\qquad
\mathbf B(z,\vartheta)=b(z)+\vartheta\,\beta(z),
\end{equation}
\begin{equation}\label{eq:onshell-minus}
\mathbf X^-(\bar z,\bar\vartheta)=\bar\gamma(\bar z)+\bar\vartheta\,\bar c(\bar z),
\qquad
\bar{\mathbf B}(\bar z,\bar\vartheta)=\bar b(\bar z)+\bar\vartheta\,\bar\beta(\bar z),
\end{equation}
with operator products
\begin{equation}\label{eq:ope-holomorphic}
\beta(z)\gamma(w)\sim \frac{1}{z-w},
\qquad
b(z)c(w)\sim \frac{1}{z-w},
\end{equation}
\begin{equation}\label{eq:ope-antiholomorphic}
\bar\beta(\bar z)\bar\gamma(\bar w)\sim \frac{1}{\bar z-\bar w},
\qquad
\bar b(\bar z)\bar c(\bar w)\sim \frac{1}{\bar z-\bar w}.
\end{equation}
The component conformal weights are
\begin{equation}\label{eq:component-weights}
h(\gamma)=0,
\qquad
h(\beta)=1,
\qquad
h(c)=h(b)=\frac{1}{2},
\end{equation}
and similarly in the antiholomorphic sector. Hence the bosonic $(\beta,\gamma)$ system contributes $c=2$, while the fermionic $(b,c)$ system contributes $c=1$, so
\begin{equation}\label{eq:longitudinal-central-charge}
c_{+-}=2+1=3.
\end{equation}
while the eight transverse bosons and fermions contribute $12$, so
\begin{equation}\label{eq:total-central-charge}
c_{\mathrm{matter}}=15.
\end{equation}
Thus the matter system is exactly that of a critical type-II RNS string, written in first-order variables. The first two terms in \eqref{eq:flat-action} are the Poisson/BF core, while the $1/\Aeff$ term keeps a finite string scale rather than collapsing the theory to a purely topological model.

It is useful to say explicitly what the finite $\Aeff$ deformation does and does not do. Because the last term in \eqref{eq:flat-action} does not involve $\mathbf B$ or $\bar{\mathbf B}$, varying those fields still gives the chirality constraints $\bar D\mathbf X^+=0$ and $D\mathbf X^-=0$; the complementary equations $\bar D\mathbf B=0$ and $D\bar{\mathbf B}=0$ come from varying $\mathbf X^\pm$. So the deformation does not change the classical holomorphicity constraints, even though it is not physically trivial: it fixes the normalization of global energies and chemical potentials, and the same $\Aeff$ reappears later in the genus-one energy formula \eqref{eq:go-energy}. Its coefficient is also not a free choice: the relative normalization of the BF term and the $1/\Aeff$ deformation is fixed by the original Gomis--Ooguri scaling limit. In the present note, however, I treat that finite-$\Aeff$ term only as a benchmark deformation inherited from \cite{gomis2000nonrelativisticclosedstringtheory}, not as part of the exact $\Sym^N(\bR^8)$ duality claim itself.

\section{Patchwise Definition on a Riemann Surface}
Let $C$ be a target Riemann surface. Choose holomorphic charts $U_a\subset C$ with local coordinate $u_a$ and local metric representative
\begin{equation}\label{eq:local-target-metric}
ds_C^2=e^{2\omega_a(u_a,\bar u_a)}\,du_a\,d\bar u_a.
\end{equation}
On the worldsheet we introduce, in each chart, superfields
\begin{equation}\label{eq:local-target-fields}
\mathbf X^+_a,\quad \mathbf X^-_a,\quad \mathbf B_a,\quad \bar{\mathbf B}_a
\end{equation}
and define the local longitudinal action
\begin{equation}\label{eq:curved-local-action}
\begin{aligned}
S^{(a)}_{\mathrm{long}}
=
\frac{1}{2\pi}\int d^2z\,d\vartheta\,d\bar\vartheta\,
\left[
\mathbf B_a\,\bar D\mathbf X^+_a
+\bar{\mathbf B}_a\,D\mathbf X^-_a
+\frac{e^{2\omega_a(\mathbf X_a^+,\mathbf X_a^-)}}{4\Aeff}\,
D\mathbf X^+_a\,\bar D\mathbf X^-_a
\right].
\end{aligned}
\end{equation}
The transverse action $S_\perp$ is unchanged, since the transverse target remains $\bR^8$.

This is precisely the place where the curved $\beta\gamma$ machinery reviewed by Nekrasov \cite{nekrasov2005curvedbetagammasystems} is essential. The first-order fields do not patch as ordinary scalars; they patch as a coordinate and its conjugate one-form under target holomorphic coordinate changes. Without this machinery one only has a local action in each chart, not a globally defined worldsheet theory on $C$.

On an overlap $U_a\cap U_b$, let
\begin{equation}\label{eq:target-transition-functions}
u_b=f_{ba}(u_a),
\qquad
\bar u_b=\bar f_{ba}(\bar u_a),
\end{equation}
with $f_{ba}$ holomorphic. The superfields are patched by
\begin{equation}\label{eq:superfield-patching}
\mathbf X^+_b=f_{ba}(\mathbf X^+_a),
\qquad
\mathbf X^-_b=\bar f_{ba}(\mathbf X^-_a),
\end{equation}
\begin{equation}\label{eq:beta-patching}
\mathbf B_b=\big(f'_{ba}(\mathbf X^+_a)\big)^{-1}\mathbf B_a,
\qquad
\bar{\mathbf B}_b=\big(\bar f'_{ba}(\mathbf X^-_a)\big)^{-1}\bar{\mathbf B}_a.
\end{equation}
This is the natural superfield version of a curved $\beta\gamma$ system. Indeed,
\begin{equation}\label{eq:bf-patching-check}
\mathbf B_b\,\bar D\mathbf X^+_b
=
\big(f'_{ba}(\mathbf X^+_a)\big)^{-1}\mathbf B_a\,
f'_{ba}(\mathbf X^+_a)\bar D\mathbf X^+_a
=
\mathbf B_a\,\bar D\mathbf X^+_a,
\end{equation}
and similarly for the antiholomorphic term. The metric factor transforms as
\begin{equation}\label{eq:metric-transformation}
e^{2\omega_b(u_b,\bar u_b)}
=
e^{2\omega_a(u_a,\bar u_a)}
\left|\frac{du_a}{du_b}\right|^2,
\end{equation}
so the last term in $S^{(a)}_{\mathrm{long}}$ also patches correctly:
\begin{equation}\label{eq:kinetic-patching-check}
e^{2\omega_b}D\mathbf X^+_b\,\bar D\mathbf X^-_b
=
e^{2\omega_a}D\mathbf X^+_a\,\bar D\mathbf X^-_a.
\end{equation}
The chirality constraints are also coordinate-independent:
\begin{equation}\label{eq:chirality-patching}
\bar D\mathbf X^+_b=f'_{ba}(\mathbf X^+_a)\bar D\mathbf X^+_a,
\qquad
D\mathbf X^-_b=\bar f'_{ba}(\mathbf X^-_a)D\mathbf X^-_a.
\end{equation}
So the statement that the bosonic map $\gamma:\Sigma\to C$ is holomorphic is globally meaningful and does not depend on the choice of target chart.
The cocycle condition on triple overlaps follows automatically from
\begin{equation}\label{eq:cocycle}
f_{ca}=f_{cb}\circ f_{ba}
\end{equation}
together with the chain rule. Moreover, the Euclidean reality condition \eqref{eq:euclidean-reality} is compatible with \eqref{eq:superfield-patching} because for a genuine real two-manifold $C$ the antiholomorphic transition function is the complex conjugate $\bar f_{ba}$ of $f_{ba}$. If $\gamma:\Sigma\to C$ denotes the bosonic map underlying the superfield $\mathbf X^+$, then the component fields $c$ and $b$ in \eqref{eq:onshell-plus} are naturally sections of $\gamma^*(TC)$ and $\gamma^*(T^*C)$.

It is also useful to be explicit about the fermions. The fermionic components $c$ and $\bar c$ transform as sections of $\gamma^*(TC)$ and $\gamma^*(\overline{TC})$, while $b$ and $\bar b$ transform as sections of the dual bundles. They are not target-space spinors. So the patching data above do not require an independent spin structure on $C$; the genuine spin-structure subtlety appears later when $C$ itself is a spacetime torus and one chooses periodic or antiperiodic boundary conditions for spacetime fermions around its cycles.

One can also check that the curved deformation does not spoil the on-shell chirality of $\mathbf B$. Varying $\mathbf X^+_a$ gives
\begin{equation}\label{eq:curved-b-eom}
\bar D\mathbf B_a
=
\frac{1}{4\Aeff}
\left[
D\!\left(e^{2\omega_a}\bar D\mathbf X^-_a\right)
-\partial_{+}\!\big(e^{2\omega_a}\big)\,D\mathbf X^+_a\,\bar D\mathbf X^-_a
\right],
\end{equation}
where $\partial_+$ denotes differentiation with respect to the holomorphic target coordinate $u_a$. Using the first-order constraints $\bar D\mathbf X^+_a=0$ and $D\mathbf X^-_a=0$, together with $D\bar D\mathbf X^-_a=-\bar DD\mathbf X^-_a=0$, the right-hand side of \eqref{eq:curved-b-eom} vanishes on shell. Hence $\bar D\mathbf B_a=0$, and similarly $D\bar{\mathbf B}_a=0$, also hold in the curved theory.

Therefore the local first-order theory defines a globally consistent \emph{classical} worldsheet action on any target Riemann surface $C$. This classical patching statement is derived in the note; it is not merely conjectural. Its classical solution locus is the moduli space of holomorphic maps $\gamma:\Sigma\to C$. For $C=T^2$ this locus reduces to the familiar discrete sum over winding data, whereas for general $C$ it is a genuine moduli space of holomorphic maps. Any extension of the torus free-energy check away from $C=T^2$ would therefore be expected to replace the discrete $(w,n)$ sum by an integral, or at least a sum over connected components, of this holomorphic-map moduli space together with the corresponding fluctuation determinants.

\section{Quantum Status and the Target-Space Weyl Question}
The first-order Poisson/BF core,
\begin{equation}\label{eq:bf-core}
\frac{1}{2\pi}\int d^2z\,d\vartheta\,d\bar\vartheta\,
\left(
\mathbf B\,\bar D\mathbf X^+
+\bar{\mathbf B}\,D\mathbf X^-
\right),
\end{equation}
does not involve the target metric at all. The only place where the chosen local representative
\begin{equation}\label{eq:target-weyl-representative}
ds_C^2=e^{2\omega}du\,d\bar u
\end{equation}
enters is the finite string-tension deformation
\begin{equation}\label{eq:metric-deformation}
\frac{1}{8\pi \Aeff}\int d^2z\,d\vartheta\,d\bar\vartheta\,
e^{2\omega(\mathbf X^+,\mathbf X^-)}D\mathbf X^+\,\bar D\mathbf X^-.
\end{equation}
In that strict Poisson-sigma model, the target Weyl representative drops out exactly. This is the precise sense in which the worldsheet already knows that the candidate dual should depend only on the conformal structure of the two-dimensional spacetime $C$, as one expects for a CFT. The finite-$\Aeff$ deformation is therefore a separate issue: it reintroduces a chosen representative \eqref{eq:target-weyl-representative}, but only through the term \eqref{eq:metric-deformation}. In the present note I use that deformed system below only as a flat-space genus-one benchmark.

There are two distinct issues. First, the composite operator $e^{2\omega(\mathbf X^+,\mathbf X^-)}$ in \eqref{eq:metric-deformation} requires a regularization and normal-ordering prescription. Because the bulk $X^+X^-$ OPE is regular in the first-order variables, the short-distance singularities are milder than in an ordinary second-order sigma model, but finite local counterterms can still renormalize the curved deformation.

The mechanism behind this improved UV behavior is simple. In the strict BF limit obtained by dropping the $1/\Aeff$ term, the only singular OPEs are $\beta(z)\gamma(w)\sim 1/(z-w)$, $b(z)c(w)\sim 1/(z-w)$, and their antiholomorphic counterparts; the mixed OPE $X^+(z,\bar z)X^-(w,\bar w)$ is regular. So the composite operator $e^{2\omega(X^+,X^-)}$ does not already carry the standard second-order normal-ordering singularity. Such singularities arise only after the finite-$\Aeff$ deformation is turned on, which is why the quantum problem is milder than in the usual sigma-model presentation, even though it is not absent.

Second, one expects, at minimum, the usual curved-$\beta\gamma$ measure anomaly of the type emphasized in \cite{nekrasov2005curvedbetagammasystems}. For a target Riemann surface $C$, its topological part is controlled by the first Chern class of $TC$, hence by
\begin{equation}\label{eq:target-euler}
\int_C c_1(TC)=\chi(C)=2-2g_C.
\end{equation}
Here $g_C$ is the genus of the target Riemann surface $C$. So for $C=S^2$ the topological obstruction is certainly nontrivial, for $C=T^2$ it vanishes, and for $g_C>1$ it is again nonzero. This does not by itself determine the full local counterterm problem, but it does show that the quantum completion of the curved first-order system is not automatic. In a full string construction this may require a local counterterm or dilaton-like worldsheet curvature coupling of the form
\begin{equation}\label{eq:dilaton-like-coupling}
S_\Phi=\frac{1}{4\pi}\int_\Sigma \sqrt{g_{\rm ws}}\,R^{(2)}_{\rm ws}\,\Phi(X^+,X^-).
\end{equation}
Here $g_{\rm ws}$ is a chosen metric on the worldsheet $\Sigma$, $R^{(2)}_{\rm ws}$ is its scalar curvature, and $\Phi$ is a possible target-space scalar counterterm. The present note does not determine that term.

A full quantum construction would also require a renormalized worldsheet stress tensor and supercurrent on curved $C$. In flat space they are those of the standard first-order RNS system and give the critical matter central charge \eqref{eq:total-central-charge}. On curved $C$, however, the deformation \eqref{eq:metric-deformation} changes the nonchiral dynamics and can generate $\omega$-dependent composite corrections to amplitudes and to the renormalized stress tensor. The companion BRST analysis mentioned above argues that the global chiral BRST operator itself survives for the full super longitudinal multiplet. What remains open in the present note is the amplitude-level use of that BRST structure together with the renormalized nonchiral dynamics of the finite-$\Aeff$ deformation.

This is the right place to distinguish three different notions:
\begin{itemize}
\item Worldsheet conformal invariance is the statement that the local matter system has the critical central charge \eqref{eq:total-central-charge}.
\item Exact Weyl-structure independence of the Poisson/BF core is the algebraic statement that the representative $e^{2\omega}$ does not appear in \eqref{eq:bf-core} at all.
\item Target-space Weyl invariance of the deformed finite-$\Aeff$ system is the stronger statement that changing
\begin{equation}\label{eq:target-weyl-rescaling}
\omega\longmapsto \omega+\sigma
\end{equation}
does not change the physical BRST data after all required counterterms are included.
\end{itemize}
The current note establishes the first two statements, but not the third. The honest claim is therefore narrower than in the earlier draft: curved $\beta\gamma$ patching under holomorphic coordinate changes is explicit and essential, and the pure Poisson/BF core manifestly forgets the target Weyl representative, whereas the full quantum completion of the deformed finite-$\Aeff$ system remains to be proved after the anomaly problem and the normal ordering of \eqref{eq:metric-deformation} are understood.

\section[Conjectural Duality to SymN(R8)]{Conjectural Duality to $\Sym^N(\bR^8)$}
The proposed dual field theory is the symmetric-orbifold SCFT
\begin{equation}\label{eq:dual-orbifold}
\Sym^N(\bR^8)
\end{equation}
placed on the same two-dimensional spacetime $C$. Concretely, this is the $S_N$ orbifold of $N$ copies of the free $(8,8)$ $\bR^8$ sigma model. The duality claim itself is conjectural. In the present note I restrict attention to the exact orbifold CFT \eqref{eq:dual-orbifold} and to observables intrinsic to that theory.

The simplest dictionary is:
\begin{itemize}
\item The target Riemann surface $C$ of the first-order string is the physical spacetime on which the two-dimensional CFT is defined.
\item The eight free transverse bosons and fermions of the string are the same noncompact $\bR^8$ seed degrees of freedom that appear in each copy of the orbifold SCFT.
\item If a perturbative closed-string genus expansion exists, then it should reproduce the large-$N$ expansion of connected exact-orbifold observables. The relative suppression by extra handles is therefore part of the desired dictionary, but the precise identification of $g_s$ with a definite power of $N$ depends on the normalization of the observable under study and will not be fixed a priori in this note.
\item The exact orbifold should be compared to the Poisson/BF first-order string with eight free transverse multiplets. Beyond the genus-one free-energy benchmark, the relevant orbifold-side data are the intrinsic twist-sector correlators and OPE coefficients of the exact symmetric product, not a deformation of the orbifold action.
\end{itemize}

The proposal is therefore simply this: the Poisson/BF first-order worldsheet system, together with the eight free transverse multiplets, should reproduce exact orbifold data of $\Sym^N(\bR^8)$ when both are formulated on the same two-dimensional spacetime $C$. The finite-$\Aeff$ Gomis--Ooguri deformation will still appear below as a useful flat-torus benchmark, but I do not interpret it here as the defining structure of the exact $\Sym^N(\bR^8)$ duality itself. Likewise, the $1/N$ expansion discussed in this note belongs to the exact symmetric-orbifold observables themselves; it should not be conflated with matrix string theory, which would require a further deformation problem not studied here.

In particular, I do \emph{not} study in this note any further deformation of the Poisson-sigma model toward matrix string theory or toward the full two-dimensional $(8,8)$ SYM. That would be a separate problem.

\section[First Check: Genus One and Large-N Orbifold Free Energy]{First Check: Genus One and the Large-$N$ Orbifold Free Energy}
Take the target spacetime to be a Euclidean thermal torus with temporal period $\beta=T^{-1}$ and spatial circle of circumference $2\pi R$,
\begin{equation}\label{eq:thermal-target}
t_E\sim t_E+\beta,
\qquad
x\sim x+2\pi R.
\end{equation}
Here $T$ is the temperature and $R$ is the target-space spatial radius. Since the seed theory on $\bR^8$ is noncompact, the partition functions in this subsection are understood per unit transverse volume, equivalently with the center-of-mass zero modes divided out. The natural large-$N$ quantity to compare with the genus-one string free energy is then not the full canonical partition function of $\Sym^N(\bR^8)$, which contains pieces growing with $N$, but its stable order-$N^0$ single-cycle contribution. Equivalently, one may package this data in a grand-canonical generating function with fugacity $p$ for cycle length and then take the plethystic logarithm. This is the standard second-quantized string interpretation of symmetric-product orbifolds \cite{dijkgraaf1997ellipticgenerasymmetricproducts}. The orbifold manipulations in this subsection are derived directly in the note, while the worldsheet answer quoted later is imported from \cite{gomis2000nonrelativisticclosedstringtheory}. For the physical thermal spin structure $[\nu_t,\nu_x]=[1,0]$, the multiplicity matching will also be derived explicitly below.

Let $\mc H_1^{[\nu_t,\nu_x]}$ be the Hilbert space of one copy of the $\bR^8$ SCFT on a circle of circumference $2\pi R$, with spacetime fermion boundary conditions labeled by
\begin{equation}\label{eq:target-spin-structure}
\nu_t,\nu_x\in \{0,1\},
\end{equation}
where $\nu=0$ means periodic and $\nu=1$ means antiperiodic. In operator language, $\nu_x$ specifies the spatial-circle Hilbert space, while $\nu_t$ specifies whether the Euclidean-time trace is ordinary ($\nu_t=1$) or twisted by $(-1)^F$ ($\nu_t=0$). The thermal free energy corresponds to $\nu_t=1$. Write the corresponding seed trace as
\begin{equation}\label{eq:seed-trace}
Z_1^{[\nu_t,\nu_x]}(\beta,\theta)
=
\mathrm{Tr}_{\mc H_1^{[\nu_t,\nu_x]}}
\exp\!\left[
-\beta \frac{L_0+\bar L_0}{R}
+i\theta(L_0-\bar L_0)
\right]
=
\sum_{h,\bar h} D^{[\nu_t,\nu_x]}(h,\bar h)\,
e^{-\beta(h+\bar h)/R+i\theta(h-\bar h)}.
\end{equation}
Here $L_0$ and $\bar L_0$ are the left- and right-moving Virasoro zero modes of a single copy of the $\bR^8$ SCFT, $\theta$ is a bookkeeping angle for level matching, and $D^{[\nu_t,\nu_x]}(h,\bar h)$ counts seed states of conformal weights $(h,\bar h)$ in the chosen spacetime spin structure. I use $h$ and $\bar h$ to denote the actual numbers appearing in the Boltzmann factor, including the sector-dependent zero-point energies appropriate to the chosen NS/R and GSO conventions. Any overall vacuum normalization that is independent of the cycle fugacity $p$ is left implicit.

For the actual comparison to the Gomis--Ooguri thermal free energy, the physically relevant spatial spin structure is periodic,
\begin{equation}\label{eq:physical-spatial-spin}
\nu_x=0,
\end{equation}
because this is the natural supersymmetric choice on the spacetime circle. In this case the $w$-cycle twisted sector has the standard symmetric-orbifold long-string covering-space description \cite{dijkgraaf1997matrixstring,arutyunov1998orbifoldscattering}. Let $c_{\rm seed}=12$ be the chiral central charge of one copy of the $\bR^8$ SCFT, and let $(\Delta,\bar\Delta)$ denote the plane conformal weights of a seed operator. Under the $w$-fold covering map
\begin{equation}\label{eq:covering-map}
z=t^w,
\end{equation}
the corresponding twisted-sector operator has weights
\begin{equation}\label{eq:twisted-weight-map}
\Delta_w-\frac{c_{\rm seed}}{24}
=
\frac{1}{w}\left(\Delta-\frac{c_{\rm seed}}{24}\right),
\qquad
\bar\Delta_w-\frac{c_{\rm seed}}{24}
=
\frac{1}{w}\left(\bar\Delta-\frac{c_{\rm seed}}{24}\right).
\end{equation}
Equivalently, the cylinder energies above the Ramond vacuum scale as $1/w$. With the standard Dijkgraaf--Verlinde--Verlinde lift of the cyclic permutation to the fermions, the periodic seed sector is Ramond and its vacuum already has $\Delta_0=\bar\Delta_0=c_{\rm seed}/24=1/2$, so the square-root Jacobian from the covering map is absorbed into the usual twisted-vacuum energy shift and the long-string Hilbert space is again in the Ramond sector rather than acquiring an extra parity flip for even $w$. An alternative even-$w$ lift would shift the operator-channel sector and would require a separate analysis. Throughout this note I adopt the standard DVV choice. Therefore the twisted-sector multiplicities relevant to the thermal comparison are in fact $w$-independent:
\begin{equation}\label{eq:w-independent-degeneracy}
D_w^{[1,0]}(h,\bar h)=D_{\rm RR}^{\mathrm{seed}}(h,\bar h).
\end{equation}
Here $D_{\rm RR}^{\mathrm{seed}}(h,\bar h)$ is the degeneracy of one copy of the $\bR^8$ SCFT with periodic spatial fermions and the ordinary thermal trace. The label ``RR'' refers to the fact that both left- and right-moving Hilbert spaces are in their Ramond sectors along the spatial circle; it does \emph{not} mean that the Euclidean-time boundary condition is also periodic.
It is convenient to package the same seed Hilbert-space data as the specialized trace
\begin{equation}\label{eq:seed-rr-trace}
Z_{\rm RR}^{\mathrm{seed}}(\beta,\theta)
:=
Z_1^{[1,0]}(\beta,\theta)
=
\sum_{h,\bar h} D_{\rm RR}^{\mathrm{seed}}(h,\bar h)\,
e^{-\beta(h+\bar h)/R+i\theta(h-\bar h)}.
\end{equation}
To make this trace fully explicit, define
\begin{equation}\label{eq:seed-thermal-modulus}
q=e^{-\beta/R+i\theta}=e^{2\pi i\tau_{\rm seed}},
\qquad
\bar q=e^{-\beta/R-i\theta}=e^{-2\pi i\bar\tau_{\rm seed}},
\qquad
\tau_{\rm seed}:=\frac{\theta+i\beta/R}{2\pi}.
\end{equation}
If $V_8$ denotes the volume of the noncompact transverse $\bR^8$, then the free seed trace per unit transverse volume is
\begin{equation}\label{eq:seed-rr-factorized}
\frac{Z_{\rm RR}^{\mathrm{seed}}(\beta,\theta)}{V_8}
=
\int_{\bR^8}\frac{d^8k}{(2\pi)^8}\,
e^{-\beta \Aeff k^2/(2R)}\,
\chi^{\mathrm{osc}}_{\rm RR}(q)\,
\bar\chi^{\mathrm{osc}}_{\rm RR}(\bar q).
\end{equation}
Evaluating the Gaussian integral gives
\begin{equation}\label{eq:seed-rr-gaussian}
\frac{Z_{\rm RR}^{\mathrm{seed}}(\beta,\theta)}{V_8}
=
\left(\frac{R}{2\pi \beta \Aeff}\right)^4
\chi^{\mathrm{osc}}_{\rm RR}(q)\,
\bar\chi^{\mathrm{osc}}_{\rm RR}(\bar q).
\end{equation}
Here $k\in \bR^8$ is the transverse momentum and
\begin{equation}\label{eq:seed-rr-oscillator}
\chi^{\mathrm{osc}}_{\rm RR}(q)
=
16\prod_{n=1}^\infty \frac{(1+q^n)^8}{(1-q^n)^8}
=
\frac{\vartheta_2(\tau_{\rm seed})^4}{\eta(\tau_{\rm seed})^{12}},
\end{equation}
with the same formula antiholomorphically for $\bar\chi^{\mathrm{osc}}_{\rm RR}(\bar q)$. The factor $16$ is the degeneracy of the eight left-moving Ramond zero modes; the right-moving sector contributes the same factor.
The first few oscillator coefficients are
\begin{equation}\label{eq:seed-rr-oscillator-expansion}
\chi^{\mathrm{osc}}_{\rm RR}(q)
=
16+256q+2304q^2+15360q^3+84224q^4+O(q^5).
\end{equation}
So the full seed trace begins with a $16\times 16=256$-state Ramond ground multiplet, followed by the expected tower of left- and right-moving oscillator excitations.
The same free transverse system can also be described in path-integral language, for one fixed diagonal spin structure of the free transverse matter system, by torus partition functions per unit transverse volume,
\begin{equation}\label{eq:transverse-path-integral-spin}
\frac{Z_{\perp}^{[\alpha,\beta]}(\tau,\bar\tau)}{V_8}
=
\frac{1}{(4\pi^2 \Aeff\,\mathrm{Im}\,\tau)^4}\,
\frac{\vartheta\!\begin{bmatrix}\alpha\\ \beta\end{bmatrix}\!(0|\tau)^4}{\eta(\tau)^{12}}
\frac{\overline{\vartheta\!\begin{bmatrix}\alpha\\ \beta\end{bmatrix}\!(0|\tau)^4}}{\bar\eta(\bar\tau)^{12}},
\qquad
\alpha,\beta\in\left\{0,\frac12\right\}.
\end{equation}
Here $\tau$ is the Euclidean worldsheet torus modulus, while $\alpha$ and $\beta$ label fermion boundary conditions around chosen torus cycles; this $\beta$ is a theta-characteristic label, not the inverse temperature appearing in \eqref{eq:thermal-target}. The formula \eqref{eq:transverse-path-integral-spin} is the partition function in one \emph{fixed} spin structure before any GSO sum. This notation should not be confused with the operator-channel character \eqref{eq:seed-rr-trace}: once one chooses which torus cycle is interpreted as Euclidean time, modular transformations can exchange the various theta characteristics. In the present genus-one comparison I work in the operator channel adapted to the long-string Hamiltonian \eqref{eq:long-string-hamiltonian}, so the explicit seed character \eqref{eq:seed-rr-trace}--\eqref{eq:seed-rr-oscillator-expansion} is the relevant object.

Denote by $\mc H_w$ the Hilbert space of a single length-$w$ twisted sector. A twisted sector built from a single cycle of length $w$ is a ``long string'' whose effective spatial circle has circumference $2\pi wR$. Its Hamiltonian is therefore
\begin{equation}\label{eq:long-string-hamiltonian}
H_w=\frac{L_0+\bar L_0}{wR}.
\end{equation}
Projecting onto the $\mathbb Z_w$-invariant subspace gives
\begin{equation}\label{eq:cyclic-projector}
P_w=\frac{1}{w}\sum_{n=0}^{w-1} g^n,
\qquad
g\cdot |h,\bar h\rangle
=
e^{2\pi i(h-\bar h)/w}|h,\bar h\rangle.
\end{equation}
Hence the thermal partition function of one cycle of length $w$, weighted by fugacity $p^w$, is
\begin{equation}\label{eq:one-cycle-trace}
\begin{aligned}
Z^{\mathrm{1\mbox{-}cycle}}_w(\beta,p)
&=
\mathrm{Tr}_{\mc H_w}\!\left(
P_w\,p^w e^{-\beta H_w}
\right)
\\
&=
\frac{p^w}{w}\sum_{n=0}^{w-1}\sum_{h,\bar h}D_w^{[\nu_t,\nu_x]}(h,\bar h)\,
\exp\!\left[
-\beta \frac{h+\bar h}{wR}
+2\pi i \frac{n}{w}(h-\bar h)
\right].
\end{aligned}
\end{equation}
The sum over $n$ imposes
\begin{equation}\label{eq:orbifold-level-matching}
h-\bar h\equiv 0 \pmod w,
\end{equation}
which is the usual long-string level-matching condition. Equivalently, it is simply the cyclic-orbifold projection onto states invariant under the generator $g$ of the length-$w$ twisted sector.
In the physical thermal spin structure, \eqref{eq:w-independent-degeneracy} and \eqref{eq:seed-rr-trace} turn \eqref{eq:one-cycle-trace} into the compact character formula
\begin{equation}\label{eq:one-cycle-trace-thermal}
Z^{\mathrm{1\mbox{-}cycle}}_w(\beta,p)\Big|_{[1,0]}
=
\frac{p^w}{w}\sum_{n=0}^{w-1}
Z_{\rm RR}^{\mathrm{seed}}\!\left(\frac{\beta}{w},\frac{2\pi n}{w}\right).
\end{equation}

The order-$N^0$ free energy is the standard plethystic free-gas answer built from these single-cycle states:
\begin{equation}\label{eq:orbifold-free-energy-sum}
\begin{aligned}
F^{(0)}_{\Sym}(\beta,p)
&=
-T\sum_{m=1}^\infty \frac{1}{m}
\sum_{w=1}^\infty Z^{\mathrm{1\mbox{-}cycle}}_w(m\beta,p^m)
\\
&=
-T\sum_{m=1}^\infty \sum_{w=1}^\infty \sum_{n=0}^{w-1}
\frac{p^{mw}}{wm}\sum_{h,\bar h}D_w^{[\nu_t,\nu_x]}(h,\bar h)\,
\exp\!\left[
-m\beta \frac{h+\bar h}{wR}
+2\pi i \frac{n}{w}(h-\bar h)
\right].
\end{aligned}
\end{equation}
Using $\log(1-x)=-\sum_{m\ge1}x^m/m$, this becomes
\begin{equation}\label{eq:orbifold-free-energy-log}
F^{(0)}_{\Sym}(\beta,p)
=
T\sum_{w=1}^\infty
\sum_{\substack{h,\bar h\\ h-\bar h\in w\mathbb Z}}
D_w^{[\nu_t,\nu_x]}(h,\bar h)\,
\log\!\left(
1-p^w e^{-\beta(h+\bar h)/(wR)}
\right).
\end{equation}
Equation \eqref{eq:orbifold-free-energy-log} is the derived orbifold answer in the present note. The universal $\log(1-x)$ is the standard symmetric-orbifold plethystic logarithm for cycle sectors. The spacetime fermion boundary conditions change the sector-dependent multiplicities $D_w^{[\nu_t,\nu_x]}(h,\bar h)$, not the combinatorial cycle factor itself.
There is therefore no separate $\log(1+x)$ for fermionic seed states. The symmetric product always symmetrizes copies of the full seed theory, while any fermion signs are already encoded inside the one-cycle trace itself.

In the physical thermal spin structure, \eqref{eq:one-cycle-trace-thermal} gives the more explicit character-level formula
\begin{equation}\label{eq:orbifold-free-energy-character}
F^{(0)}_{\Sym}(\beta,p)\Big|_{[1,0]}
=
-T\sum_{m=1}^\infty \sum_{w=1}^\infty \frac{p^{mw}}{wm}
\sum_{n=0}^{w-1}
Z_{\rm RR}^{\mathrm{seed}}\!\left(\frac{m\beta}{w},\frac{2\pi n}{w}\right),
\end{equation}
and equivalently, substituting \eqref{eq:w-independent-degeneracy} into \eqref{eq:orbifold-free-energy-log} gives the explicit logarithmic formula
\begin{equation}\label{eq:orbifold-free-energy-thermal}
F^{(0)}_{\Sym}(\beta,p)\Big|_{[1,0]}
=
T\sum_{w=1}^\infty
\sum_{\substack{h,\bar h\\ h-\bar h\in w\mathbb Z}}
D_{\rm RR}^{\mathrm{seed}}(h,\bar h)\,
\log\!\left(
1-p^w e^{-\beta(h+\bar h)/(wR)}
\right).
\end{equation}

Now compare with the genus-one worldsheet result of Gomis and Ooguri \cite{gomis2000nonrelativisticclosedstringtheory}. The following formula is quoted from their one-loop free-energy computation, rewritten in the present notation. Their torus path integral localizes to holomorphic maps from the worldsheet torus to the target thermal torus and gives
\begin{equation}\label{eq:go-free-energy-sum}
\begin{aligned}
F_{\mathrm{GO}}(T)
&=
-\sum_{m=1}^\infty \sum_{w=1}^\infty \sum_{n}
\frac{T}{wm}\sum_{h,\bar h}D^{\mathrm{GO}}_w(h,\bar h)\,
\exp\!\left[
-\frac{m}{T}\left(
\frac{wR}{2\Aeff}+\frac{h+\bar h}{wR}
\right)
+2\pi i \frac{n}{w}(h-\bar h)
\right],
\end{aligned}
\end{equation}
which they resum as
\begin{equation}\label{eq:go-free-energy-log}
F_{\mathrm{GO}}(T)
=
T\sum_{w=1}^\infty
\sum_{\substack{h,\bar h\\ h-\bar h\in w\mathbb Z}}
D^{\mathrm{GO}}_w(h,\bar h)\,
\log\!\left(
1-e^{-E(w,h,\bar h)/T}
\right),
\end{equation}
with
\begin{equation}\label{eq:go-energy}
E(w,h,\bar h)
=
\frac{wR}{2\Aeff}+\frac{h+\bar h}{wR}.
\end{equation}
In the notation of \cite{gomis2000nonrelativisticclosedstringtheory}, the quantities $h$ and $\bar h$ already include both transverse momenta and transverse oscillator excitations:
\begin{equation}\label{eq:go-transverse-weights}
h=\frac{\Aeff k^2}{4}+N,
\qquad
\bar h=\frac{\Aeff k^2}{4}+\bar N.
\end{equation}
Here $k\in \bR^8$ is the transverse momentum, while $N$ and $\bar N$ are the left- and right-moving transverse oscillator levels. Thus the multiplicity factor $D_w^{\mathrm{GO}}(h,\bar h)$ appearing in the Gomis--Ooguri answer is simply their transverse multiplicity $D(h,\bar h)$, already independent of $w$, written in the same seed Hilbert-space variables used above. For the thermal comparison at hand, I identify this multiplicity with the same transverse free $\bR^8$ lightcone Hilbert space used in \eqref{eq:seed-rr-trace}: eight bosons together with eight fermions in the Ramond spatial sector, evaluated in the ordinary thermal trace. The finite-temperature GSO choice itself is part of the quoted Gomis--Ooguri result; the present point is only that, after that choice is made, the surviving multiplicity is the same seed degeneracy. Thus
\begin{equation}\label{eq:go-degeneracy-identification}
D_w^{\mathrm{GO}}(h,\bar h)=D_{\rm RR}^{\mathrm{seed}}(h,\bar h).
\end{equation}
Because the phase in \eqref{eq:go-free-energy-sum} depends only on $n$ modulo $w$, one may choose representatives $n=0,\dots,w-1$. Using \eqref{eq:seed-rr-trace} and \eqref{eq:go-degeneracy-identification}, the quoted Gomis--Ooguri formula can then be rewritten as
\begin{equation}\label{eq:go-free-energy-character}
F_{\mathrm{GO}}(T)
=
-T\sum_{m=1}^\infty \sum_{w=1}^\infty \frac{e^{-m\beta wR/(2\Aeff)}}{wm}
\sum_{n=0}^{w-1}
Z_{\rm RR}^{\mathrm{seed}}\!\left(\frac{m\beta}{w},\frac{2\pi n}{w}\right),
\end{equation}
where $\beta=T^{-1}$.
If desired, one may now substitute the explicit free-field expression \eqref{eq:seed-rr-factorized}--\eqref{eq:seed-rr-oscillator} into either \eqref{eq:orbifold-free-energy-character} or \eqref{eq:go-free-energy-character}. This produces exactly the same momentum integral over $k$ and the same Ramond oscillator product in both formulas.
One can also repackage the same statement in the path-integral notation \eqref{eq:transverse-path-integral-spin}. To do so uniformly for arbitrary target-torus spin structures, however, one must track carefully the induced theta characteristic of the holomorphic map together with the modular transformation back to the operator channel used here. I have not attempted that more global bookkeeping in the present note, because for the physical thermal sector $[\nu_t,\nu_x]=[1,0]$ the operator-channel argument already suffices.
The algebraic dependence on $w$, $(h,\bar h)$, and the Boltzmann factor then matches the orbifold answer after the identification
\begin{equation}\label{eq:chemical-potential}
p=e^{-\beta\mu},
\qquad
\mu=\frac{R}{2\Aeff}.
\end{equation}
Here $\mu$ is the chemical potential conjugate to cycle length, equivalently to target winding in the first-order-string interpretation. The point of the quoted Gomis--Ooguri derivation is that, for this flat-torus benchmark, the finite-$\Aeff$ deformation is unusually simple: after the $\beta_0$ integral localizes the torus modulus, the longitudinal $(\beta,\gamma)$ non-zero modes cancel against their fermionic $(b,c)$ partner system, so the deformation contributes only the instanton factor $e^{-m\beta wR/(2\Aeff)}$ associated with the holomorphic map. On the exact-orbifold side, a multi-cycle state with cycle lengths $\{w_a\}$ then acquires the weight
\begin{equation}\label{eq:cosmological-constant-weight}
\prod_a p^{w_a}
=
e^{-\beta\mu \sum_a w_a}
=
e^{-\beta\mu N}.
\end{equation}
Thus, in the grand-canonical packaging natural for the genus-one free energy, the benchmark finite-$\Aeff$ deformation is equivalent simply to adding a cosmological constant, or chemical potential, conjugate to the total copy number $N$. At fixed $N$ it does not change the intrinsic local dynamics of the exact $\Sym^N(\bR^8)$ CFT; it only changes the ensemble used to organize the free energy. In the physical thermal spin structure $[\nu_t,\nu_x]=[1,0]$, and with the standard DVV lift adopted above, the covering-map argument gives
\par
Equivalently, for this quoted flat-torus one-loop benchmark, the finite $\partial X^+\bar\partial X^-$ deformation acts only through the grand-canonical weight $e^{-\beta\mu N}$. It does not modify the intrinsic one-cycle seed spectrum or the orbifold projection data entering \eqref{eq:one-cycle-trace-thermal}--\eqref{eq:orbifold-free-energy-thermal}; those are still the exact symmetric-orbifold building blocks. This simplification is special to the genus-one free-energy computation of \cite{gomis2000nonrelativisticclosedstringtheory}, where the longitudinal non-zero modes cancel after localization, and I do not promote it here to a statement about arbitrary observables on general target curves.
\par
\begin{equation}\label{eq:degeneracy-match}
D_w^{[1,0]}(h,\bar h)=D^{\mathrm{GO}}_w(h,\bar h),
\end{equation}
because both sides are equal to the same seed Ramond-sector degeneracy $D_{\rm RR}^{\mathrm{seed}}$ by \eqref{eq:w-independent-degeneracy} and \eqref{eq:go-degeneracy-identification}. Thus the multiplicity matching required for the thermal test is established within that standard long-string convention. Comparing \eqref{eq:orbifold-free-energy-character} with \eqref{eq:go-free-energy-character}, one finds a term-by-term equality once \eqref{eq:chemical-potential} is imposed. Equivalently, after substituting \eqref{eq:chemical-potential} into \eqref{eq:orbifold-free-energy-thermal} the orbifold free energy becomes
\begin{equation}\label{eq:free-energy-match}
F^{(0)}_{\Sym}(\beta,\mu)\Big|_{[1,0]}
=
T\sum_{w=1}^\infty
\sum_{\substack{h,\bar h\\ h-\bar h\in w\mathbb Z}}
D_{\rm RR}^{\mathrm{seed}}(h,\bar h)\,
\log\!\left(
1-e^{-\beta[\mu w +(h+\bar h)/(wR)]}
\right),
\end{equation}
which then reproduces the Gomis--Ooguri answer.

This comparison is stronger than a mere agreement of final spectra. The two auxiliary sums appearing in \cite{gomis2000nonrelativisticclosedstringtheory} acquire a direct orbifold meaning:
\begin{itemize}
\item the $n$-sum is precisely the $\mathbb Z_w$ projector onto cyclically invariant states in the length-$w$ twisted sector,
\item the $m$-sum is precisely the plethystic expansion of $\log(1-x)$.
\end{itemize}
So the worldsheet localization on holomorphic maps to the target torus found by Gomis and Ooguri is mirrored, on the orbifold side, by the standard cycle decomposition of the symmetric product. In the thermal spin structure $[\nu_t,\nu_x]=[1,0]$, and within the standard DVV lift, the match is therefore numerical as well as structural.

It is worth being precise about the extent of this nontriviality. The genuinely nontrivial part of the test is the longitudinal/stringy reorganization: the holomorphic-map sum appearing in the quoted genus-one Gomis--Ooguri formula, including the linear winding energy $wR/(2\Aeff)$, the $\mathbb Z_w$ level-matching projector, and the $m$-sum over plethystic images, is reproduced exactly by the large-$N$ single-cycle orbifold free energy after the identification \eqref{eq:chemical-potential}. That is a real constraint on the proposed duality.

At the same time, this genus-one/$N^0$ test is not yet decisive. Both sides use the same free transverse $\bR^8$ matter system, so once the standard DVV long-string lift is chosen, the detailed coefficient matching is still largely kinematical. In other words, the test shows that the first-order string reorganizes the free orbifold data in the correct string-theoretic way, but it does not yet probe genuinely interacting joining/splitting data or other observables that would distinguish the proposal more sharply.

There is still an additional subtlety for \emph{other} target-torus spin structures: if one wants a uniform formula for arbitrary $[\nu_t,\nu_x]$, then one must track carefully how the covering map acts on fermions in NS sectors and how $(-1)^F$ insertions are represented in the orbifold trace. That more general bookkeeping remains worthwhile, but it is no longer needed for the concrete thermal test carried out here.

There is one conceptual caveat. The exact formula above is naturally grand canonical in cycle length, because the linear piece $wR/(2\Aeff)$ is represented by the fugacity $p^w$. If one insists on the strictly canonical fixed-$N$ partition function, one should extract the coefficient of $p^N$ at the end. The resulting large-$N$ asymptotic expansion is still an expansion of exact symmetric-orbifold data, not a matrix-string deformation. Its order-$N^0$ part is controlled by the same single-cycle building blocks written above, while genuinely new tests beyond genus one should come from other exact orbifold observables, such as intrinsic twist-sector correlators, rather than from the free partition function alone.

\section{Beyond Genus One: Canonical Three-Point Data on \texorpdfstring{$S^2$}{S2}}
The genus-one thermal free energy is naturally organized grand canonically in cycle length. The first genuinely new observables of the exact orbifold, however, are local correlators at fixed rank $N$ and fixed cycle data. The next exact test is therefore a canonical pair-of-pants amplitude on the three-punctured sphere.

\subsection{Pair-of-Pants Target and Ramification Data}

At tree level the relevant target is the three-punctured sphere
\begin{equation}\label{eq:sphere-spacetime}
C_{0,3}:=S^2\setminus\{0,1,\infty\},
\end{equation}
not a deformation of the orbifold action. Because the strict Poisson/BF core forgets the target Weyl representative, one may equally well think of \eqref{eq:sphere-spacetime} as a sphere with three marked points or choose a representative metric with three semi-infinite cylindrical ends. In that cylindrical picture one inserts a state on each asymptotic tube.
Figure~\ref{fig:pair-of-pants-target} summarizes these two equivalent target-space pictures. Here each $\Psi_i$ denotes a general asymptotic state on the $i$-th target tube, not necessarily a single long string.

\begin{figure}[t]
\centering
\begin{minipage}{0.46\textwidth}
\centering
\begin{tikzpicture}[scale=0.92, line cap=round, line join=round]
\draw[line width=19pt, black]
  (0.05,0.05) .. controls (-0.55,-0.45) and (-1.00,-1.00) .. (-1.55,-1.75);
\draw[line width=15pt, gray!15]
  (0.05,0.05) .. controls (-0.55,-0.45) and (-1.00,-1.00) .. (-1.55,-1.75);

\draw[line width=19pt, black]
  (0.05,0.10) .. controls (0.02,0.80) and (0.08,1.35) .. (0.22,2.20);
\draw[line width=15pt, gray!15]
  (0.05,0.10) .. controls (0.02,0.80) and (0.08,1.35) .. (0.22,2.20);

\draw[line width=19pt, black]
  (0.18,-0.02) .. controls (0.90,-0.05) and (1.55,-0.45) .. (2.38,-1.05);
\draw[line width=15pt, gray!15]
  (0.18,-0.02) .. controls (0.90,-0.05) and (1.55,-0.45) .. (2.38,-1.05);

\fill[white] (-1.70,-1.93) ellipse [x radius=0.34, y radius=0.16, rotate=-38];
\draw[thick] (-1.70,-1.93) ellipse [x radius=0.34, y radius=0.16, rotate=-38];
\fill[white] (0.24,2.48) ellipse [x radius=0.30, y radius=0.14];
\draw[thick] (0.24,2.48) ellipse [x radius=0.30, y radius=0.14];
\fill[white] (2.62,-1.20) ellipse [x radius=0.33, y radius=0.15, rotate=-8];
\draw[thick] (2.62,-1.20) ellipse [x radius=0.33, y radius=0.15, rotate=-8];

\draw[->, thick] (-2.55,-2.55) -- (-1.95,-2.08);
\draw[->, thick] (0.24,3.05) -- (0.24,2.64);
\draw[->, thick] (3.35,-1.45) -- (2.92,-1.28);
\node at (-2.78,-2.78) {$\Psi_1$};
\node at (0.24,3.30) {$\Psi_2$};
\node at (3.62,-1.50) {$\Psi_3$};
\node[align=center, text width=2.6cm] at (0.35,-2.85) {$C_{0,3}$ with three semi-infinite tubes};
\end{tikzpicture}
\end{minipage}
\hfill
\begin{minipage}{0.46\textwidth}
\centering
\begin{tikzpicture}[scale=1.0, line cap=round, line join=round]
\shade[ball color=gray!12, opacity=0.45] (0,0) circle (1.55);
\draw[thick] (0,0) circle (1.55);
\fill (0,1.2) circle (0.06);
\fill (-1.05,-0.55) circle (0.06);
\fill (1.15,-0.45) circle (0.06);
\node[above] at (0,1.2) {$\infty,\lambda_3$};
\node[left] at (-1.05,-0.55) {$0,\lambda_1$};
\node[right] at (1.15,-0.45) {$1,\lambda_2$};
\node at (0,-2.1) {$S^2$ with three marked points};
\node at (0,1.85) {$C_{0,3}=S^2\setminus\{0,1,\infty\}$};
\end{tikzpicture}
\end{minipage}
\caption{Two equivalent target-space pictures for the next exact-orbifold observable. Because the Poisson/BF core forgets the target Weyl representative, the three-punctured sphere $C_{0,3}$ may be viewed either as a pair of pants with three semi-infinite cylinders carrying general asymptotic states $\Psi_i$, or as the compact sphere with three marked points labeled by ramification profiles $\lambda_i$. Each $\Psi_i$ may represent a multi-string state with profile $\lambda_i$; the single-cycle case is the special choice $\lambda_i=(w_i)$.}
\label{fig:pair-of-pants-target}
\end{figure}

A general exact-orbifold state on one tube need not be a single long string; it can carry an arbitrary cycle decomposition
\begin{equation}\label{eq:ramification-profile}
\lambda_i=(w_{i,1},\dots,w_{i,\ell_i}),
\qquad
\sum_{a=1}^{\ell_i} w_{i,a}\le N,
\end{equation}
where $\lambda_i$ records only the active constituent strings on the $i$-th tube. The omitted $N-\sum_a w_{i,a}$ copies stay in the identity sector and are left implicit.
Thus the most general tree-level observable is a three-point amplitude between states of prescribed ramification profile on the three tubes. I first work out the simplest nontrivial case in which each external state is a single-cycle twisted-sector state, so each profile is a one-part partition $\lambda_i=(w_i)$. After compactifying the cylindrical ends back to the marked points $(0,1,\infty)$ on $S^2$, this is equivalently the canonical three-point function of single-cycle twist operators. The general NS--NS sewn-cover extension is returned to later in this section.

\subsection{Exact Orbifold Three-Point Input}

At the orbifold point, define the normalized single-cycle class operator by
\begin{equation}\label{eq:class-operator}
\widehat{\sigma}_{[w]}
:=
\frac{1}{\sqrt{|[w]|_N}}
\sum_{g\in [w]}\sigma_g,
\qquad
|[w]|_N=\frac{N!}{w(N-w)!},
\end{equation}
where $[w]\subset S_N$ is the conjugacy class of $w$-cycles. For the connected three-point function associated with degree-$d$ covers of genus $g$, the standard covering-space description of symmetric-product orbifolds takes the form \cite{arutyunov1998orbifoldscattering,lunin2001correlationorbifolds,lunin2002threepointorbifolds,pakman2009diagramssymmetricorbifold,pakman2009extremalhurwitz}
\begin{equation}\label{eq:orbifold-three-point}
\mc C_{123}^{(g)}(N)
:=
\left\langle
\widehat{\sigma}_{[w_1]}(0)\,
\widehat{\sigma}_{[w_2]}(1)\,
\widehat{\sigma}_{[w_3]}(\infty)
\right\rangle_{g}^{\mathrm{conn}}
=
\frac{N!}{(N-d)!}\,
\frac{
H_d^{(g)}(w_1,w_2,w_3)\,
\mc C_{\mathrm{seed}}^{(g)}(w_1,w_2,w_3)
}{
\sqrt{|[w_1]|_N\,|[w_2]|_N\,|[w_3]|_N}
}.
\end{equation}
Here $d$ is the number of active copies. In the present note I will simply \emph{quote} the exact orbifold formula \eqref{eq:orbifold-three-point} rather than rederive it. The underlying covering-space derivation, including the Liouville/conformal-anomaly contribution and the normalization of bosonic twist operators, is carried out explicitly in \cite[Secs.~5--6]{lunin2001correlationorbifolds}. For the supersymmetric single-cycle chiral operators relevant here, \cite[Sec.~4]{lunin2002threepointorbifolds} writes the normalized three-point function as a ratio of current/spin-field correlators on the cover multiplied by the exponential of a difference of Liouville actions, with the Liouville part identified with the bosonic twist contribution from \cite{lunin2001correlationorbifolds}. The later diagrammatic/Hurwitz reorganization is reviewed in \cite{pakman2009diagramssymmetricorbifold}. In this quoted orbifold formula, $H_d^{(g)}$ should be understood as the weighted Hurwitz count
\begin{equation}\label{eq:weighted-hurwitz-count}
H_d^{(g)}(w_1,w_2,w_3)
:=
\sum_{[f]}
\frac{1}{|\mathrm{Aut}(f)|},
\end{equation}
while $\mc C_{\mathrm{seed}}^{(g)}$ denotes the reduced seed-theory factor appearing in that quoted orbifold result. The important point for the present note is that \eqref{eq:orbifold-three-point} is an orbifold-side input imported from the literature; its string-side analogue is part of what must be checked rather than assumed. For three branch points, the degree is constrained by Riemann--Hurwitz:
\begin{equation}\label{eq:riemann-hurwitz-three-point}
2-2g
=
2d-\sum_{i=1}^3 (w_i-1),
\qquad
d=\frac{w_1+w_2+w_3-1}{2}-g.
\end{equation}
The symbols $N$, $w_i$, and $d$ play different roles. Here $N$ is the total copy number of the orbifold $\Sym^N(\bR^8)$, $w_i$ is the cycle length inserted at the $i$-th marked point, and $d$ is the number of copies that are actually active in one connected cover contributing to \eqref{eq:orbifold-three-point}. The remaining $N-d$ copies stay in the untwisted identity sector. In particular, the connected three-point function does \emph{not} require $w_1+w_2+w_3=N$; the only finite-$N$ constraint is that the degree determined by \eqref{eq:riemann-hurwitz-three-point} obeys $d\le N$.
In particular, for fixed cycle lengths $(w_1,w_2,w_3)$ and large $N$, the leading contribution comes from $g=0$. Writing
\begin{equation}\label{eq:tree-level-degree}
d_0:=\frac{w_1+w_2+w_3-1}{2},
\end{equation}
one finds directly from \eqref{eq:orbifold-three-point} that
\begin{equation}\label{eq:orbifold-three-point-leading}
\mc C_{123}^{(0)}(N)
=
N^{-1/2}
\Big[
\sqrt{w_1w_2w_3}\,
H_{d_0}^{(0)}(w_1,w_2,w_3)\,
\mc C_{\mathrm{seed}}^{(0)}(w_1,w_2,w_3)
+O(N^{-1})
\Big].
\end{equation}
Thus the first nontrivial large-$N$ comparison is indeed a genuine tree-level worldsheet problem: the leading orbifold coefficient comes from genus-zero covers and scales as $N^{-1/2}$.

It is worth emphasizing that the factor $\sqrt{w_1w_2w_3}$ in \eqref{eq:orbifold-three-point-leading} is already a nontrivial structural fact. A priori the leading normalization of the orbifold three-point function could have been an arbitrary joint function of $(w_1,w_2,w_3)$. Instead, the exact orbifold answer organizes itself so that the leading local normalization factorizes puncture-by-puncture,
\[
\sqrt{w_1w_2w_3}=\prod_{i=1}^3 \sqrt{w_i}.
\]
This is precisely the pattern suggested by the rigid pair-of-pants worldsheet picture, where one would expect the leading local normalization to be attached independently to the three asymptotic tubes. Of course this factorization does \emph{not} trivialize the full correlator: the Hurwitz multiplicity $H_{d_0}^{(0)}(w_1,w_2,w_3)$ and the reduced seed-theory factor $\mc C_{\mathrm{seed}}^{(0)}(w_1,w_2,w_3)$ remain genuinely collective data of the whole three-point function. The point is only that the exact orbifold result already exhibits the puncture-local factorization pattern that the worldsheet construction would naturally predict for the leading normalization sector.

This is the right exact-orbifold observable to compare to the first-order string beyond genus one. It is already a canonical fixed-$N$ quantity, so unlike the torus free energy it does not structurally require a grand-canonical fugacity. One may still study its large-$N$ asymptotic expansion, but that expansion is part of the exact $\Sym^N(\bR^8)$ CFT itself. Grand-canonical generating functions may be useful for organizing an infinite family of such correlators, but they are optional bookkeeping rather than part of the definition of one fixed three-point function.

\subsection{Worldsheet-CFT Setup on \texorpdfstring{$C_{0,3}$}{C0,3}}

On the worldsheet side, the tree-level problem should likewise be formulated on the punctured target $C_{0,3}$ with specified asymptotic states on its three cylindrical ends. On the orbifold side, compactifying the $i$-th tube back to a marked point produces the exact-orbifold state space $\mc H^{\rm orb}_{\lambda_i}$ with ramification profile $\lambda_i$. On the string side, the corresponding object is an asymptotic state space $\mc H^{\rm str}_{z_i}$ attached to the $i$-th cylindrical end of $C_{0,3}$. A precise duality statement therefore requires maps
\begin{equation}\label{eq:tube-state-dictionary}
\iota_i:\mc H^{\rm orb}_{\lambda_i}\to \mc H^{\rm str}_{z_i},
\end{equation}
so that an orbifold state $\Psi_i^{\rm orb}\in \mc H^{\rm orb}_{\lambda_i}$ is compared to the corresponding asymptotic string state $\Psi_i:=\iota_i(\Psi_i^{\rm orb})\in \mc H^{\rm str}_{z_i}$. In the present note I keep this dictionary formal and use $\Psi_i$ for the string-side asymptotic state. The corresponding string observable is the trilinear pairing
\begin{equation}\label{eq:pair-of-pants-amplitude}
\mc A^{\rm str}_{C_{0,3}}(\Psi_1,\Psi_2,\Psi_3).
\end{equation}
For the connected single-cycle three-point function, the worldsheet side does \emph{not} geometrize all $N$ orbifold labels at once. Instead, the three external winding numbers $(w_1,w_2,w_3)$ determine an active degree-$d_0$ cover with $d_0=(w_1+w_2+w_3-1)/2$. Only those $d_0$ active copies participate in the connected branched cover. The remaining $N-d_0$ orbifold copies stay in the untwisted identity sector and do not produce additional target-space cylinders on $C_{0,3}$. Their only role in the present string description is the finite-$N$ combinatorial one: the active degree-$d_0$ cover can be embedded into the $N$ physical labels in many ways.
For NS--NS external states, separate companion derivations now fix the exact finite-$N$ normalization of \eqref{eq:tube-state-dictionary} both in the lowest single-cycle sector and for general active profiles $\lambda_i$. What remains formal at this stage of the note is only the compactified local puncture operator for a general multi-string state. The sewn-cover derivation later in this section will nevertheless determine the fixed-cover weight $\mc W_f$ for arbitrary NS--NS active profiles.

At the level of local operator algebra, the relevant BRST problem is no longer open. A companion analysis recorded separately in \texttt{BRST-curved.tex} shows that, for the full super longitudinal multiplet, the bosonic curved-$\beta\gamma$ obstruction is cancelled by its fermionic partner and the standard type-IIB BRST current patches globally on any target curve. In the present note I therefore treat that global BRST operator as established input and focus only on the explicit sphere vertex operators and the resulting tree-level amplitude.

To keep the longitudinal matter fermions distinct from the reparametrization ghosts, from this point on I rename the component fields in \eqref{eq:onshell-plus} and \eqref{eq:onshell-minus} by
\begin{equation}\label{eq:longitudinal-fermion-rename}
\psi^+:=c,
\qquad
\rho:=b,
\qquad
\bar\psi^-:=\bar c,
\qquad
\bar\rho:=\bar b.
\end{equation}
Thus $(\gamma,\beta)$ and $(\psi^+,\rho)$ are the longitudinal matter fields, while $(c_{\rm gh},b_{\rm gh})$ and the bosonized superghosts $(\xi_{\gh},\eta_{\gh},\phi_{\gh})$ belong to the standard RNS ghost system.

Expressed in the language of the worldsheet CFT, the tree-level object one wants is a sphere correlator of three BRST vertex operators in the fixed target background $C_{0,3}$. After choosing superghost pictures $(q_i,\bar q_i)$ with
\begin{equation}\label{eq:picture-balance}
q_1+q_2+q_3=-2,
\qquad
\bar q_1+\bar q_2+\bar q_3=-2,
\end{equation}
and fixing the worldsheet punctures $\zeta_i$ by the $\mathrm{PSL}(2,\bC)$ automorphism of $\Sigma\simeq S^2$, one writes
\begin{equation}\label{eq:pair-of-pants-cft-correlator}
\mc A^{\rm str}_{C_{0,3}}(\Psi_1,\Psi_2,\Psi_3)
=
\sum_{\mathfrak s}
\left\langle
c_{\rm gh}\tilde c_{\rm gh}\,\mc V_{\Psi_1,\mathfrak s}^{(q_1,\bar q_1)}(\zeta_1,\bar\zeta_1)\,
c_{\rm gh}\tilde c_{\rm gh}\,\mc V_{\Psi_2,\mathfrak s}^{(q_2,\bar q_2)}(\zeta_2,\bar\zeta_2)\,
c_{\rm gh}\tilde c_{\rm gh}\,\mc V_{\Psi_3,\mathfrak s}^{(q_3,\bar q_3)}(\zeta_3,\bar\zeta_3)
\right\rangle_{\Sigma=S^2,\mathfrak s}.
\end{equation}
Here $\mathfrak s$ labels the map sector of the worldsheet CFT in the fixed target background $C_{0,3}$. For the supersymmetric single-cycle chiral operators discussed in this section, I use the standard NS--NS choice
\begin{equation}\label{eq:sphere-picture-choice}
(q_1,\bar q_1)=(q_2,\bar q_2)=(-1,-1),
\qquad
(q_3,\bar q_3)=(0,0),
\end{equation}
which obeys \eqref{eq:picture-balance}. On the sphere there is no residual worldsheet moduli integral after fixing three insertion points.

\subsection{Explicit Longitudinal Vertex Operators}

Let $u$ be the standard complex coordinate on the compact target sphere with punctures at
\[
z_1=0,\qquad z_2=1,\qquad z_3=\infty.
\]
Near the three punctures I choose the local tube coordinates
\begin{equation}\label{eq:target-tube-coordinate}
\xi_1:=-\log u,
\qquad
\xi_2:=-\log(u-1),
\qquad
\xi_3:=\log u=-\log(1/u),
\end{equation}
and similarly $\bar\xi_i$ antiholomorphically. Writing $\xi_i=s_i+i\phi_i$, the angular variable $\phi_i$ is the circle coordinate of the $i$-th semi-infinite target tube and obeys $\phi_i\sim \phi_i+2\pi$.

The curved first-order system does not allow one to use the bare $\beta$ field globally inside a vertex operator, because $\beta$ patches with an affine correction. The tensorial object is the covariant momentum
\begin{equation}\label{eq:tube-covariant-momentum}
\Pi_u:=\beta_u-\Gamma_u\,\rho_u\psi_u^+,
\qquad
\bar\Pi_{\bar u}:=\bar\beta_{\bar u}-\bar\Gamma_{\bar u}\,\bar\rho_{\bar u}\bar\psi_{\bar u}^-,
\qquad
\Gamma_u:=2\partial_u\omega.
\end{equation}
Here $\omega$ is any auxiliary local target metric representative $ds_C^2=e^{2\omega}du\,d\bar u$. The companion BRST analysis shows that $\Pi_u$ and $\bar\Pi_{\bar u}$ transform as target one-forms, so in the tube charts I may define
\begin{equation}\label{eq:tube-covariant-components}
\Pi_{\xi_i}:=\frac{\partial u}{\partial \xi_i}\,\Pi_u,
\qquad
\bar\Pi_{\bar\xi_i}:=\frac{\partial \bar u}{\partial \bar\xi_i}\,\bar\Pi_{\bar u}.
\end{equation}
If one chooses the auxiliary Hermitian representative $ds_C^2=d\xi_i\,d\bar\xi_i$ in a tube chart, then $\Gamma_{\xi_i}=0$ and $\Pi_{\xi_i}$ reduces locally to the bare first-order field $\beta_{\xi_i}$. This is the precise sense in which the operator below is the curved version of the flat Gomis--Ooguri winding insertion.

Fix worldsheet insertion points $x_i\in \Sigma\simeq S^2$ above the three target punctures and choose nonintersecting branch cuts between them. Using line integrals ending at those insertion points, the longitudinal ramification operator on the $i$-th tube is
\begin{equation}\label{eq:fixed-cover-vertex-factorization}
\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i)
:=
\mc N_{w_i}
:\exp\!\Big[
i\bar\nu_i\,\xi_i\!\big(X^+(x_i,\bar x_i)\big)
-w_i\!\int^{x_i}\!\Pi_{\xi_i}
+i\nu_i\,\bar\xi_i\!\big(X^-(x_i,\bar x_i)\big)
-w_i\!\int^{\bar x_i}\!\bar\Pi_{\bar\xi_i}
\Big]:.
\end{equation}
The numbers $(\nu_i,\bar\nu_i)$ are the tube momenta conjugate to translations along the $i$-th cylinder. For the lowest winding state relevant to the class-normalized single-cycle chiral operator, I set
\begin{equation}\label{eq:lowest-longitudinal-state}
\Sigma^{\rm long}_{w_i}
:=
\Sigma^{\rm long}_{w_i,0,0}.
\end{equation}

Because $\Pi_{\xi_i}(t)\,\xi_i(X^+(x_i))\sim 1/(t-x_i)$ and likewise antiholomorphically, the operator \eqref{eq:fixed-cover-vertex-factorization} obeys the local OPEs
\begin{equation}\label{eq:longitudinal-local-opes}
\begin{aligned}
\xi_i\!\big(X^+(t,\bar t)\big)\,\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i)
&\sim
-\,w_i\log(t-x_i)\,\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i),
\\
\Pi_{\xi_i}(t)\,\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i)
&\sim
\frac{i\bar\nu_i}{t-x_i}\,
\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i),
\end{aligned}
\end{equation}
with the analogous antiholomorphic formulas
\[
\begin{aligned}
\bar\xi_i\!\big(X^-(t,\bar t)\big)\,\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i)
&\sim
-\,w_i\log(\bar t-\bar x_i)\,\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i),
\\
\bar\Pi_{\bar\xi_i}(\bar t)\,\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i)
&\sim
\frac{i\nu_i}{\bar t-\bar x_i}\,
\Sigma^{\rm long}_{w_i,\nu_i,\bar\nu_i}(x_i,\bar x_i).
\end{aligned}
\]
For the lowest state \eqref{eq:lowest-longitudinal-state}, differentiating the first OPE gives the desired winding singularity
\begin{equation}\label{eq:tube-winding-ope}
\begin{aligned}
\partial \xi_i\!\big(X^+(t)\big)\,
\Sigma^{\rm long}_{w_i}(x_i,\bar x_i)
&\sim
-\,\frac{w_i}{t-x_i}\,
\Sigma^{\rm long}_{w_i}(x_i,\bar x_i),
\\
\bar\partial \bar\xi_i\!\big(X^-(\bar t)\big)\,
\Sigma^{\rm long}_{w_i}(x_i,\bar x_i)
&\sim
-\,\frac{w_i}{\bar t-\bar x_i}\,
\Sigma^{\rm long}_{w_i}(x_i,\bar x_i).
\end{aligned}
\end{equation}
Equivalently,
\begin{equation}\label{eq:tube-winding-charge}
\begin{aligned}
W_i\,\Sigma^{\rm long}_{w_i}
&:=
-\,\frac{1}{2\pi i}\oint \partial \xi_i\!\big(X^+\big)\,
\Sigma^{\rm long}_{w_i}
\\
&=
w_i\,\Sigma^{\rm long}_{w_i},
\end{aligned}
\end{equation}
and likewise antiholomorphically. Equation \eqref{eq:tube-winding-ope} is simply the operator-language version of the branch law
\begin{equation}\label{eq:single-string-tube-winding}
u-z_i=t_i^{\,w_i}
\qquad\Longleftrightarrow\qquad
\xi_i=-\,w_i\log t_i,
\end{equation}
so going once around the worldsheet preimage $t_i\mapsto e^{2\pi i}t_i$ shifts the target-tube angle by $\phi_i\mapsto \phi_i+2\pi w_i$. In this precise sense the state created by $\Sigma^{\rm long}_{w_i}$ is a winding-$w_i$ string state with respect to the circle of the $i$-th target tube.

At the level of asymptotic Hilbert spaces, the corresponding single-string state takes the tensor-product form
\begin{equation}\label{eq:single-string-state-factorization}
\left|\Psi_{w_i,\chi_i}\right\rangle_i
=
\left|w_i\right\rangle_i^{\rm long}\otimes \left|\chi_i\right\rangle_i^\perp
\in
\mc H^{\rm str}_{z_i},
\end{equation}
where $\left|w_i\right\rangle_i^{\rm long}$ is created by the lowest longitudinal operator \eqref{eq:lowest-longitudinal-state} and $\left|\chi_i\right\rangle_i^\perp$ is a chosen one-copy seed state of the transverse $\bR^8$ SCFT. When the transverse seed state is fixed once and for all, I abbreviate $\Psi_{w_i,\chi_i}$ to $\Psi_{w_i}$.

\subsection{BRST Closure of the Lowest NS--NS Vertex}

The global existence of the curved-target BRST current is imported from the companion note \texttt{BRST-curved.tex}. What is still required locally is the actual cohomology calculation for the specific sphere vertex used here. Throughout this subsection I work in the standard small Hilbert space and in the usual relative closed-string complex, so the state obeys
\[
\eta_{\gh,0}=\bar\eta_{\gh,0}=0,
\qquad
b_{{\rm gh},0}^-:=b_{{\rm gh},0}-\bar b_{{\rm gh},0}=0,
\qquad
L_0^-:=L_0-\bar L_0=0.
\]

Besides the covariant momentum components \eqref{eq:tube-covariant-components}, the fermionic partner also has tube components
\begin{equation}\label{eq:tube-fermion-components}
\psi_{\xi_i}^+:=\frac{\partial \xi_i}{\partial u}\,\psi_u^+,
\qquad
\rho_{\xi_i}:=\frac{\partial u}{\partial \xi_i}\,\rho_u,
\end{equation}
and similarly $\bar\psi_{\bar\xi_i}^-$ and $\bar\rho_{\bar\xi_i}$ antiholomorphically. In the local Hermitian representative $ds_C^2=d\xi_i\,d\bar\xi_i$, where $\Gamma_{\xi_i}=0$, the longitudinal matter generators are therefore
\[
\begin{aligned}
G_{+-}(t)
&=
:\!\psi_{\xi_i}^+\Pi_{\xi_i}\!:(t)+:\!\rho_{\xi_i}\partial\xi_i\!:(t),
\\
T_{+-}(t)
&=
-:\!\Pi_{\xi_i}\partial\xi_i\!:(t)-\frac12:\!\rho_{\xi_i}\partial\psi_{\xi_i}^+\!:(t)+\frac12:\!(\partial\rho_{\xi_i})\psi_{\xi_i}^+\!:(t).
\end{aligned}
\]
For the lowest state \eqref{eq:lowest-longitudinal-state}, $\Pi_{\xi_i}(t)\Sigma^{\rm long}_{w_i}(x_i,\bar x_i)$ is regular and \eqref{eq:tube-winding-ope} gives $\partial\xi_i(t)\Sigma^{\rm long}_{w_i}(x_i,\bar x_i)\sim -w_i(t-x_i)^{-1}\Sigma^{\rm long}_{w_i}(x_i,\bar x_i)$. Hence
\begin{equation}\label{eq:longitudinal-primary-ope}
\begin{aligned}
T_{+-}(t)\,\Sigma^{\rm long}_{w_i}(x_i,\bar x_i)
&\sim
\frac{1}{t-x_i}\,
\partial_{x_i}\Sigma^{\rm long}_{w_i}(x_i,\bar x_i),
\\
G_{+-}(t)\,\Sigma^{\rm long}_{w_i}(x_i,\bar x_i)
&\sim
\frac{\Theta^{\rm long}_{w_i}(x_i,\bar x_i)}{t-x_i},
\end{aligned}
\end{equation}
with the longitudinal superpartner
\begin{equation}\label{eq:longitudinal-superpartner}
\Theta^{\rm long}_{w_i}(x_i,\bar x_i)
:=
-\,w_i\,\rho_{\xi_i}(x_i)\,\Sigma^{\rm long}_{w_i}(x_i,\bar x_i),
\end{equation}
and likewise antiholomorphically
\[
\bar\Theta^{\rm long}_{w_i}(x_i,\bar x_i)
:=
-\,w_i\,\bar\rho_{\bar\xi_i}(\bar x_i)\,\Sigma^{\rm long}_{w_i}(x_i,\bar x_i).
\]
So $\Sigma^{\rm long}_{w_i}$ is a longitudinal matter primary of weight $(0,0)$; it is the bottom component of a nontrivial NS matter supermultiplet rather than an operator with trivial supercurrent OPE.

For the supersymmetric single-cycle chiral operators, let $\mc O_{\chi_i}^\perp$ be the standard one-copy transverse seed matter operator of weights $(\tfrac12,\tfrac12)$, chosen so that it is an NS superprimary:
\begin{equation}\label{eq:transverse-superprimary-ope}
\begin{aligned}
T_\perp(t)\,\mc O_{\chi_i}^\perp(x_i,\bar x_i)
&\sim
\frac{\tfrac12\,\mc O_{\chi_i}^\perp(x_i,\bar x_i)}{(t-x_i)^2}
\,+\,
\frac{\partial_{x_i}\mc O_{\chi_i}^\perp(x_i,\bar x_i)}{t-x_i},
\\
G_\perp(t)\,\mc O_{\chi_i}^\perp(x_i,\bar x_i)
&\sim
\frac{\mc O_{\chi_i}^{\perp,\downarrow}(x_i,\bar x_i)}{t-x_i},
\end{aligned}
\end{equation}
with analogous barred formulas. Define the full matter operator
\begin{equation}\label{eq:full-matter-superprimary}
\mc U_{w_i,\chi_i}
:=
\Sigma^{\rm long}_{w_i}\,\mc O_{\chi_i}^\perp.
\end{equation}
Combining \eqref{eq:longitudinal-primary-ope} and \eqref{eq:transverse-superprimary-ope} gives
\begin{equation}\label{eq:full-matter-superprimary-ope}
\begin{aligned}
T_m(t)\,\mc U_{w_i,\chi_i}(x_i,\bar x_i)
&\sim
\frac{\tfrac12\,\mc U_{w_i,\chi_i}(x_i,\bar x_i)}{(t-x_i)^2}
\,+\,
\frac{\partial_{x_i}\mc U_{w_i,\chi_i}(x_i,\bar x_i)}{t-x_i},
\\
G_m(t)\,\mc U_{w_i,\chi_i}(x_i,\bar x_i)
&\sim
\frac{\mc U_{w_i,\chi_i}^{\downarrow}(x_i,\bar x_i)}{t-x_i},
\end{aligned}
\end{equation}
where
\begin{equation}\label{eq:full-matter-superdescendant}
\mc U_{w_i,\chi_i}^{\downarrow}
:=
\Theta^{\rm long}_{w_i}\,\mc O_{\chi_i}^\perp
\,+\,
\Sigma^{\rm long}_{w_i}\,\mc O_{\chi_i}^{\perp,\downarrow},
\end{equation}
and similarly in the antiholomorphic sector. Equation \eqref{eq:full-matter-superprimary-ope} is the concrete local statement that the matter part of the sphere vertex is a weight-$(\tfrac12,\tfrac12)$ NS superprimary.

Define the usual $(-1,-1)$ representative
\begin{equation}\label{eq:longitudinal-ns-vertex}
\mc V^{(-1,-1)}_{w_i,\chi_i}
:=
\mc U_{w_i,\chi_i}\,
e^{-\phi_{\gh}-\bar\phi_{\gh}}
\;=\;
\Sigma^{\rm long}_{w_i}\,
e^{-\phi_{\gh}-\bar\phi_{\gh}}\,
\mc O_{\chi_i}^\perp.
\end{equation}
To check BRST closure explicitly, use the standard bosonized RNS current
\begin{equation}\label{eq:local-brst-current-sphere}
j_B
=
c_{\rm gh}\bigl(T_m+T_{\eta\xi}+T_\phi\bigr)
+c_{\rm gh}\partial c_{\rm gh}\,b_{\rm gh}
+\eta_{\gh}e^{\phi_{\gh}}G_m
-\eta_{\gh}\partial\eta_{\gh}\,e^{2\phi_{\gh}}b_{\rm gh},
\end{equation}
where $T_{\eta\xi}$ and $T_\phi$ are the standard stress tensors of the bosonized superghost system $(\eta_{\gh},\xi_{\gh},\phi_{\gh})$, and the same barred formula defines $\bar j_B$. The relevant ghost OPEs are
\[
b_{\rm gh}(t)c_{\rm gh}(x_i)\sim \frac{1}{t-x_i},
\qquad
T_\phi(t)e^{-\phi_{\gh}}(x_i)\sim
\frac{\tfrac12\,e^{-\phi_{\gh}}(x_i)}{(t-x_i)^2}
\,+\,
\frac{\partial e^{-\phi_{\gh}}(x_i)}{t-x_i},
\]
together with $e^{\phi_{\gh}}(t)e^{-\phi_{\gh}}(x_i)\sim (t-x_i)$ and $e^{2\phi_{\gh}}(t)e^{-\phi_{\gh}}(x_i)\sim (t-x_i)^2 e^{\phi_{\gh}}(x_i)$. Because $G_m(t)\mc U_{w_i,\chi_i}(x_i,\bar x_i)$ has only the simple pole displayed in \eqref{eq:full-matter-superprimary-ope}, the last two terms of \eqref{eq:local-brst-current-sphere} are regular on $c_{\rm gh}e^{-\phi_{\gh}}\mc U_{w_i,\chi_i}$. The double poles from $c_{\rm gh}(T_m+T_\phi)$ and from $c_{\rm gh}\partial c_{\rm gh}b_{\rm gh}$ then give
\begin{equation}\label{eq:single-string-brst-class}
j_B(t)\,c_{\rm gh}e^{-\phi_{\gh}}\mc U_{w_i,\chi_i}(x_i,\bar x_i)
\sim
\frac{\bigl(h(\mc U_{w_i,\chi_i})-\tfrac12\bigr)\,
c_{\rm gh}\partial c_{\rm gh}e^{-\phi_{\gh}}\mc U_{w_i,\chi_i}(x_i,\bar x_i)}
{t-x_i}
=0,
\end{equation}
because \eqref{eq:full-matter-superprimary-ope} gives $h(\mc U_{w_i,\chi_i})=\tfrac12$. The same argument holds antiholomorphically, so
\[
Q_{\mathrm{BRST}}
\Bigl[
c_{\rm gh}\tilde c_{\rm gh}\,\mc V^{(-1,-1)}_{w_i,\chi_i}
\Bigr]
=0.
\]
Thus the explicit $(-1,-1)$ sphere operator is BRST closed in the relative small-Hilbert-space complex.

The $(0,0)$ representative is then obtained by picture changing,
\begin{equation}\label{eq:longitudinal-zero-picture}
\mc V^{(0,0)}_{w_i,\chi_i}
:=
\mc X_{\rm PCO}\,\bar{\mc X}_{\rm PCO}\cdot
\mc V^{(-1,-1)}_{w_i,\chi_i},
\qquad
\mc X_{\rm PCO}:=\{Q,\xi_{\gh}\},
\qquad
\bar{\mc X}_{\rm PCO}:=\{\bar Q,\bar\xi_{\gh}\}.
\end{equation}
Here $Q$ and $\bar Q$ are the left- and right-moving BRST charges.
Because $Q\mc X_{\rm PCO}=\bar Q\bar{\mc X}_{\rm PCO}=0$ by nilpotency, \eqref{eq:single-string-brst-class} immediately implies that $\mc V^{(0,0)}_{w_i,\chi_i}$ is BRST closed as well. Its matter part is the superdescendant \eqref{eq:full-matter-superdescendant} and its barred partner, so picture changing \emph{does} introduce a longitudinal descendant term proportional to $\Theta^{\rm long}_{w_i}\,\mc O_{\chi_i}^\perp$. I keep the full coincident-PCO ghost completion implicit below, because the amplitude formula only needs the BRST-closed $0$-picture representative itself, not the expansion of those standard ghost terms.

With the choice \eqref{eq:sphere-picture-choice}, the fixed-target sphere amplitude therefore becomes
\begin{equation}\label{eq:fixed-cover-correlator}
\begin{aligned}
\mc A^{\rm str}_{C_{0,3}}(\Psi_{w_1,\chi_1},\Psi_{w_2,\chi_2},\Psi_{w_3,\chi_3})
&=
\sum_{\mathfrak s}
\Big\langle
c_{\rm gh}\tilde c_{\rm gh}\,\mc V^{(-1,-1)}_{w_1,\chi_1,\mathfrak s}(x_1,\bar x_1)\,
c_{\rm gh}\tilde c_{\rm gh}\,\mc V^{(-1,-1)}_{w_2,\chi_2,\mathfrak s}(x_2,\bar x_2)\,
\\
&\hspace{2cm}
c_{\rm gh}\tilde c_{\rm gh}\,\mc V^{(0,0)}_{w_3,\chi_3,\mathfrak s}(x_3,\bar x_3)
\Big\rangle_{\Sigma=S^2,\mathfrak s}.
\end{aligned}
\end{equation}
Because
\begin{equation}\label{eq:sphere-three-point-no-moduli}
\dim_{\bC}\mc M_{0,3}=0,
\qquad
n_{\mathrm{int}}=3-3=0,
\end{equation}
there are no integrated vertices and no residual moduli Jacobian after fixing three insertion points.

\subsection{Branched-Cover Localization}

After compactifying the target tubes back to the marked points $(0,1,\infty)$, the asymptotic data become ramification data. For a general multi-string state, the puncture at $z_i$ carries the profile $\lambda_i=(w_{i,1},\dots,w_{i,\ell_i})$, so the compactified map has local behavior
\begin{equation}\label{eq:local-branching-profile}
u-z_i=t_{i,a}^{\,w_{i,a}},
\qquad
a=1,\dots,\ell_i.
\end{equation}
Thus there are $\ell_i$ preimages above the $i$-th puncture, one for each constituent long string in the target-tube state. In the single-cycle case $\lambda_i=(w_i)$ studied here, there is only one preimage above each puncture and \eqref{eq:local-branching-profile} reduces to
\begin{equation}\label{eq:local-branching}
u-z_i=t_i^{\,w_i}.
\end{equation}
The lifted longitudinal field is then single-valued in $t_i$. The classical saddles are therefore holomorphic branched covers
\begin{equation}\label{eq:branched-cover-worldsheet}
f:\Sigma\to S^2
\end{equation}
with ramification data fixed by the three profiles $\lambda_i$. In the single-cycle case this specializes to $(w_1,w_2,w_3)$ with degree constrained by \eqref{eq:riemann-hurwitz-three-point}. For three marked points on $\Sigma=S^2$, there is no continuous modulus after fixing the insertion points to $(0,1,\infty)$, so the localization problem is a discrete sum over Hurwitz classes rather than a higher-dimensional moduli integral. Figure~\ref{fig:branched-cover-data} illustrates the passage from target ramification profiles to preimages on the covering worldsheet.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=1.0, line cap=round, line join=round]
\shade[ball color=gray!10, opacity=0.5] (-4.3,0) circle (1.55);
\draw[thick] (-4.3,0) circle (1.55);
\fill (-4.3,1.18) circle (0.06);
\fill (-5.35,-0.55) circle (0.06);
\fill (-3.18,-0.45) circle (0.06);
\node[above] at (-4.3,1.18) {$z_3=\infty,\ \lambda_3$};
\node[left] at (-5.35,-0.55) {$z_1=0,\ \lambda_1$};
\node[right] at (-3.18,-0.45) {$z_2=1,\ \lambda_2$};
\node at (-4.3,-2.05) {target $S^2$};

\shade[ball color=gray!10, opacity=0.5] (3.2,0) circle (1.95);
\draw[thick] (3.2,0) circle (1.95);
\fill (2.4,1.0) circle (0.06);
\fill (3.7,0.95) circle (0.06);
\fill (1.75,-0.55) circle (0.06);
\fill (2.95,-0.35) circle (0.06);
\fill (4.35,-0.45) circle (0.06);
\node[above] at (2.4,1.0) {$t_{3,1}$};
\node[above] at (3.7,0.95) {$t_{3,2}$};
\node[left] at (1.75,-0.55) {$t_{1,1}$};
\node[below] at (2.95,-0.35) {$t_{1,2}$};
\node[right] at (4.35,-0.45) {$t_{2,1}$};
\node at (3.2,-2.35) {worldsheet $\Sigma$};
\draw[->, thick] (1.1,0.2) -- (-2.25,0.2) node[midway, above] {$f$};

\draw[dashed] (2.1,1.55) -- (2.65,0.95);
\draw[dashed] (4.0,1.55) -- (3.55,0.98);
\draw[dashed] (1.3,-1.05) -- (1.8,-0.62);
\draw[dashed] (2.6,-1.35) -- (2.98,-0.42);
\draw[dashed] (4.8,-1.1) -- (4.3,-0.52);
\node at (3.2,1.85) {\small preimages of the punctures};
\node at (3.2,-2.8) {\small $u-z_i=t_{i,a}^{\,w_{i,a}}$ near each $t_{i,a}$};
\end{tikzpicture}
\caption{Compactified branched-cover picture for the pair-of-pants amplitude. A target puncture with profile $\lambda_i=(w_{i,1},\dots,w_{i,\ell_i})$ has $\ell_i$ preimages on the worldsheet, one for each constituent long string in the asymptotic state on the $i$-th tube. In the single-cycle case used for \eqref{eq:orbifold-three-point} and \eqref{eq:orbifold-three-point-leading}, each $\lambda_i=(w_i)$ and there is only one preimage above each puncture.}
\label{fig:branched-cover-data}
\end{figure}

With the explicit operator \eqref{eq:fixed-cover-vertex-factorization}, the sum over sectors $\mathfrak s$ in \eqref{eq:fixed-cover-correlator} is no longer merely formal: it is precisely the sum over branched-cover classes compatible with the three winding numbers. Thus the sphere amplitude takes the localized form
\begin{equation}\label{eq:pair-of-pants-localized}
\mc A^{\rm str}_{C_{0,3}}(\Psi_1,\Psi_2,\Psi_3)
=
\sum_{[f]\in \mathrm{Hurwitz}(\lambda_1,\lambda_2,\lambda_3)}
\mc W_f(\Psi_1,\Psi_2,\Psi_3),
\end{equation}
where the sum runs over compactified branched-cover classes and $\mc W_f$ is the full BRST-complete weight of the cover.

Even before the explicit general local vertex is known, the finite-$N$ conversion from a marked fixed-cover computation to a normalized physical NS--NS amplitude can be fixed kinematically. Write
\begin{equation}\label{eq:general-lambda-degree-main}
d_0(\lambda_1,\lambda_2,\lambda_3)
:=
1+\frac12\sum_{i=1}^3 \bigl(|\lambda_i|-\ell_i\bigr),
\qquad
|\lambda_i|:=\sum_{a=1}^{\ell_i} w_{i,a},
\end{equation}
and let
\[
\vec\chi_i:=(\chi_{i,1},\dots,\chi_{i,\ell_i}),
\]
where $\chi_{i,a}$ is the transverse seed label of the $a$-th constituent string on the $i$-th tube. Denote by $G_{\lambda_i,\vec\chi_i}$ the subgroup that permutes only those constituents with identical pairs $(w_{i,a},\chi_{i,a})$. The companion note \texttt{ASYMPTOTIC\_STATE\_MAP\_GENERAL\_LAMBDA.tex} then shows that the purely external finite-$N$ factor is
\begin{equation}\label{eq:general-lambda-external-factor-main}
\mc G_N^{\rm ext}(\lambda_1,\vec\chi_1;\lambda_2,\vec\chi_2;\lambda_3,\vec\chi_3)
=
\frac{(N)_{d_0(\lambda_1,\lambda_2,\lambda_3)}
\sqrt{
|G_{\lambda_1,\vec\chi_1}|\,
|G_{\lambda_2,\vec\chi_2}|\,
|G_{\lambda_3,\vec\chi_3}|
}}{
\sqrt{
(N)_{|\lambda_1|}\,
(N)_{|\lambda_2|}\,
(N)_{|\lambda_3|}
}},
\end{equation}
provided the connected monodromy data are admissible. Multiplying \eqref{eq:general-lambda-external-factor-main} by the local cylinder factors $\prod_{i,a}\sqrt{w_{i,a}}$ reproduces the decorated class normalization on the orbifold side. The next subsection derives the corresponding marked fixed-cover weight directly by sewing together the already-known constituent single-string NS--NS vertices on the cover.

For the leading single-cycle genus-zero comparison, let $[f]\in \mathrm{Hurwitz}_0(d_0;w_1,w_2,w_3)$ and let $x_i\in \Sigma\simeq S^2$ be the unique ramification point above the target puncture $z_i$. The fixed-cover contribution factorizes as
\begin{equation}\label{eq:fixed-cover-psm-factorization}
\mc A^{\rm str,(0)}_{123}[f]
=
\mc N^{\rm gh}_{\mathrm{sph}}\,
\mc C_f^{\rm PSM}(\Psi_{w_1}^{\rm long},\Psi_{w_2}^{\rm long},\Psi_{w_3}^{\rm long})\,
\mc C_\perp[f;\Psi_{w_1}^\perp,\Psi_{w_2}^\perp,\Psi_{w_3}^\perp],
\end{equation}
where $\mc N^{\rm gh}_{\mathrm{sph}}$ is the universal sphere ghost/superghost factor. I use the standard normalization $\mc N^{\rm gh}_{\mathrm{sph}}=1$ from now on.

The genuinely new ingredient is the reduced Poisson/BF correlator
\begin{equation}\label{eq:fixed-cover-psm-path-integral}
\mc C_f^{\rm PSM}(\Psi_{w_1}^{\rm long},\Psi_{w_2}^{\rm long},\Psi_{w_3}^{\rm long})
:=
\int_{\mathfrak s=f}
\mc D\mathbf X^\pm\,\mc D\mathbf B\,\mc D\bar{\mathbf B}\,
e^{-S_{\rm BF}^{C_{0,3}}[\mathbf X^\pm,\mathbf B,\bar{\mathbf B}]}\,
\prod_{i=1}^3 \Sigma^{\rm long}_{w_i;f}(x_i,\bar x_i),
\end{equation}
where $S_{\rm BF}^{C_{0,3}}$ is the strict Poisson/BF core \eqref{eq:bf-core} restricted to target $C_{0,3}$. Integrating out $\mathbf B$ and $\bar{\mathbf B}$ gives
\begin{equation}\label{eq:fixed-cover-psm-localization}
\mc C_f^{\rm PSM}
=
\int_{\mathfrak s=f}
\mc D\mathbf X^\pm\,
\delta[\bar D\mathbf X^+]\,\delta[D\mathbf X^-]\,
\prod_{i=1}^3 \Sigma^{\rm long}_{w_i;f}(x_i,\bar x_i),
\end{equation}
so the path integral is supported on the holomorphic branched-cover locus
\[
X^+_{\rm cl}=f,\qquad X^-_{\rm cl}=\bar f.
\]
The local OPE \eqref{eq:tube-winding-ope} makes this support condition explicit:
\begin{equation}\label{eq:psm-vertex-local-monodromy}
\xi_i\!\big(X^+(t)\big)
\sim
-\,w_i\log(t-x_i)+\text{regular},
\qquad
\bar\xi_i\!\big(X^-(\bar t)\big)
\sim
-\,w_i\log(\bar t-\bar x_i)+\text{regular},
\end{equation}
which is equivalent to the branch law
\[
u-z_i\sim (t-x_i)^{w_i},
\qquad
\bar u-\bar z_i\sim (\bar t-\bar x_i)^{w_i}.
\]

In the strict Poisson/BF core there is no separate classical instanton action on this localized support:
\begin{equation}\label{eq:psm-classical-action-zero}
S_{\rm BF}^{C_{0,3}}[f,0,0]=0.
\end{equation}
Expanding around an isolated genus-zero cover as
\[
\mathbf X^+=f+\delta \mathbf X^+,\qquad
\mathbf X^-=\bar f+\delta \mathbf X^-,
\qquad
\mathbf B=\delta \mathbf B,\qquad
\bar{\mathbf B}=\delta \bar{\mathbf B},
\]
the quadratic fluctuation action is
\begin{equation}\label{eq:psm-quadratic-fluctuation}
S_{\rm BF}^{(2)}[f]
=
\frac{1}{2\pi}\int d^2z\,d\vartheta\,d\bar\vartheta\,
\left(
\delta \mathbf B\,\bar D \delta \mathbf X^+
+
\delta \bar{\mathbf B}\,D \delta \mathbf X^-
\right).
\end{equation}
The companion BRST analysis shows that, for the full supermultiplet, the bosonic determinant line is cancelled by the fermionic partner determinant line. In the present rigid sphere problem that cancellation gives
\begin{equation}\label{eq:psm-superdet-cancellation}
\mathrm{Sdet}'\big(\bar D\oplus D\big)_{\rm long}=1.
\end{equation}
So once the local puncture normalization is fixed, the reduced Poisson/BF correlator is independent of the individual cover:
\begin{equation}\label{eq:tree-level-cover-independence}
\mc C_f^{\rm PSM}(\Psi_{w_1}^{\rm long},\Psi_{w_2}^{\rm long},\Psi_{w_3}^{\rm long})
=
\prod_{i=1}^3 \mc N_{w_i}.
\end{equation}

The transverse factor is simpler. After localizing onto the branched cover $f$, the transverse worldsheet sector is just the free $\bR^8$ seed SCFT on the same covering sphere. For the supersymmetric single-cycle chiral operators under discussion, this is exactly the reduced seed correlator imported from the orbifold covering-space calculation:
\begin{equation}\label{eq:tree-level-transverse-match}
\mc C_\perp[f;\Psi_{w_1}^\perp,\Psi_{w_2}^\perp,\Psi_{w_3}^\perp]
=
\mc C_{\mathrm{seed}}^{(0)}(w_1,w_2,w_3).
\end{equation}
In particular, for fixed branching data it is independent of the individual cover.

\subsection{Cylinder Normalization and the Sphere Three-Point Function}

The local coefficient $\mc N_w$ is fixed on the tube cylinder rather than on the three-point sphere itself. I normalize the asymptotic states by
\begin{equation}\label{eq:tube-two-point-normalization}
\left\langle \Psi_{w,\chi}^{\mathrm{out}} \,\middle|\, \Psi_{w',\chi'}^{\mathrm{in}} \right\rangle
=
\delta_{w,w'}\,\delta_{\chi,\chi'}.
\end{equation}
For the longitudinal zero-mode pair $(\xi,\Pi_\xi)$, the local uniformizing map $u-z=t^w$ contributes one Jacobian factor $1/w$ to the cylinder pairing. Equivalently,
\begin{equation}\label{eq:longitudinal-cylinder-pairing}
\left\langle
\Sigma_{w}^{\rm long,\,out}(\infty)\,
\Sigma_{w'}^{\rm long,\,in}(0)
\right\rangle_{\mathrm{cyl}}
=
\frac{|\mc N_w|^2}{w}\,\delta_{w,w'}.
\end{equation}
This is the same local Jacobian that underlies the $\sqrt{w}$ normalization of the flat Gomis--Ooguri winding operator, but here it is applied only to the local puncture tube, not to the torus free-energy prefactor. Imposing \eqref{eq:tube-two-point-normalization} gives
\begin{equation}\label{eq:local-normalization-sqrtw}
\mc N_w=\sqrt{w},
\qquad
Z_w:=|\mc N_w|^2=w.
\end{equation}
The same cylinder pairing gives the missing non-exactness statement for the BRST-closed state constructed in \eqref{eq:single-string-brst-class}. Choose the out-state in the same picture and normalize the transverse seed two-point function by
\[
\bigl\langle \mc O_{\chi}^{\perp,\,\mathrm{out}}(\infty)\,
\mc O_{\chi'}^{\perp,\,\mathrm{in}}(0)\bigr\rangle_{\mathrm{cyl}}
=
\delta_{\chi,\chi'},
\]
while the standard ghost factor
\[
\bigl\langle
c_{\rm gh}\tilde c_{\rm gh}e^{-\phi_{\gh}-\bar\phi_{\gh}}(\infty)\,
c_{\rm gh}\tilde c_{\rm gh}e^{-\phi_{\gh}-\bar\phi_{\gh}}(0)
\bigr\rangle_{\mathrm{cyl}}
\]
is nonzero. Then \eqref{eq:longitudinal-cylinder-pairing} implies
\begin{equation}\label{eq:nonexact-cylinder-pairing}
\Bigl\langle
\Psi_{w,\chi}^{\mathrm{out}}
\Bigm|
c_{\rm gh}\tilde c_{\rm gh}\,\mc V^{(-1,-1)}_{w',\chi'}(0)
\Bigr\rangle_{\mathrm{cyl}}
=
\delta_{w,w'}\,\delta_{\chi,\chi'}.
\end{equation}
If the BRST-closed state were exact,
\[
c_{\rm gh}\tilde c_{\rm gh}\,\mc V^{(-1,-1)}_{w',\chi'}(0)
=
Q_{\mathrm{BRST}}\Lambda(0),
\]
then its pairing with the BRST-closed out-state would vanish by contour deformation of $Q_{\mathrm{BRST}}$. Equation \eqref{eq:nonexact-cylinder-pairing} is nonzero, so the lowest $(-1,-1)$ state is not BRST exact. Therefore it defines a nonzero element of the relative BRST cohomology.

Substituting into \eqref{eq:tree-level-cover-independence}, the reduced longitudinal correlator becomes
\begin{equation}\label{eq:psm-rigid-cover-reduction}
\mc C_f^{\rm PSM}(\Psi_{w_1}^{\rm long},\Psi_{w_2}^{\rm long},\Psi_{w_3}^{\rm long})
=
\sqrt{w_1w_2w_3}.
\end{equation}
This is now an explicit sphere result for the strict Poisson/BF core, not a remaining ansatz.

It is convenient to summarize the fixed-cover weight as
\begin{equation}\label{eq:cover-weight-factorization}
\mc W_f(\Psi_1,\Psi_2,\Psi_3)
=
\frac{1}{|\mathrm{Aut}(f)|}\,
\sqrt{w_1w_2w_3}\,
\mc C_{\mathrm{seed}}^{(0)}(w_1,w_2,w_3),
\end{equation}
where all dependence on the individual cover now appears only through the Hurwitz weight $1/|\mathrm{Aut}(f)|$.

For the single-cycle comparison, the full genus-zero string amplitude is therefore
\begin{equation}\label{eq:tree-level-string-three-point}
\mc A^{\rm str,(0)}_{123}
:=
\mc A^{\rm str}_{C_{0,3}}(\Psi_{w_1},\Psi_{w_2},\Psi_{w_3})
=
\sum_{[f]\in \mathrm{Hurwitz}_0(d_0;w_1,w_2,w_3)}
\mc W_f(\Psi_{w_1},\Psi_{w_2},\Psi_{w_3}).
\end{equation}
Since the fixed-cover weight \eqref{eq:cover-weight-factorization} is independent of the chosen cover inside the fixed Hurwitz class, the sum collapses to
\begin{equation}\label{eq:tree-level-hurwitz-reduction}
\mc A^{\rm str,(0)}_{123}
=
\mc G_N^{\rm ext}(w_1,w_2,w_3)\,
\sqrt{w_1w_2w_3}\,
H_{d_0}^{(0)}(w_1,w_2,w_3)\,
\mc C_{\mathrm{seed}}^{(0)}(w_1,w_2,w_3).
\end{equation}
Here $\mc G_N^{\rm ext}(w_1,w_2,w_3)$ is the purely external finite-$N$ factor that converts the marked tube state used in the local worldsheet calculation into the normalized physical asymptotic state. It is not part of the localized Poisson/BF dynamics.

More precisely, the worldsheet computation above uses the marked tube state created by the local puncture operator, so the local factor $\sqrt{w_i}$ is already accounted for puncture by puncture. The separate note \texttt{ASYMPTOTIC\_STATE\_MAP.tex} then derives the remaining finite-$N$ external-state factor by averaging those marked states over ordered injections of the active sheet set into the $N$ physical labels. The result is
\begin{equation}\label{eq:tree-level-normalization-match}
\mc G_N^{\rm ext}(w_1,w_2,w_3)
=
\frac{N!}{(N-d_0)!}\,
\sqrt{
\frac{(N-w_1)!\,(N-w_2)!\,(N-w_3)!}{(N!)^3}
}.
\end{equation}
Using the class-size formula contained in \eqref{eq:class-operator}, this may equally well be written as
\begin{equation}\label{eq:external-class-factor}
\mc G_N^{\rm ext}(w_1,w_2,w_3)
=
\frac{N!}{(N-d_0)!}\,
\frac{1}{\sqrt{w_1w_2w_3\,|[w_1]|_N\,|[w_2]|_N\,|[w_3]|_N}}.
\end{equation}
Equations \eqref{eq:tree-level-hurwitz-reduction} and \eqref{eq:tree-level-normalization-match} therefore give the exact genus-zero string answer in this sector. Comparing that derived string expression with the quoted orbifold coefficient \eqref{eq:orbifold-three-point}, one finds
\begin{equation}
\mc A^{\rm str,(0)}_{123}
=
\mc C_{123}^{(0)}(N).
\end{equation}

The structure of this comparison is important. The worldsheet computation itself fixes the local puncture factor $\prod_i\sqrt{w_i}$, the Hurwitz weighting, and the seed-theory factor. The remaining exact finite-$N$ factor \eqref{eq:tree-level-normalization-match} is the external-state conversion encoded by the asymptotic-state map \eqref{eq:tube-state-dictionary}; in the present project it is no longer fixed by coefficient matching, but derived separately from finite-$N$ tube-state counting in \texttt{ASYMPTOTIC\_STATE\_MAP.tex}. In particular, the nontrivial local part of the orbifold coefficient is now reproduced directly by the explicit longitudinal vertex operator, while the remaining $N$-dependence comes from the exact combinatorics of embedding a connected degree-$d_0$ active-sheet cover into the $N$ physical labels.

In the dilute large-$N$ regime with fixed $(w_1,w_2,w_3)$ and $d_0=(w_1+w_2+w_3-1)/2$, \eqref{eq:tree-level-normalization-match} expands as
\begin{equation}\label{eq:tree-level-large-n-prefactor}
\mc G_N^{\rm ext}(w_1,w_2,w_3)
=
N^{-1/2}
\left[
1+\frac{1}{N}
\left(
\frac14\sum_{i=1}^3 w_i(w_i-1)-\frac12 d_0(d_0-1)
\right)
+O(N^{-2})
\right].
\end{equation}
Substituting this into \eqref{eq:tree-level-hurwitz-reduction} gives
\begin{equation}\label{eq:tree-level-large-n-match}
\mc A^{\rm str,(0)}_{123}
=
N^{-1/2}
\Big[
\sqrt{w_1w_2w_3}\,
H_{d_0}^{(0)}(w_1,w_2,w_3)\,
\mc C_{\mathrm{seed}}^{(0)}(w_1,w_2,w_3)
+O(N^{-1})
\Big],
\end{equation}
which is exactly the large-$N$ orbifold form \eqref{eq:orbifold-three-point-leading}. So the first genuine large-$N$ test beyond the torus free energy is passed in the strict Poisson/BF sphere computation: the longitudinal worldsheet dynamics supplies the puncture-local factor $\sqrt{w_1w_2w_3}$ and the branched-cover sum supplies the Hurwitz factor, while the standard transverse seed correlator reproduces the remaining one-copy data.

\subsection{General NS--NS Profiles by Sewn Covers}

The remaining caveat after the single-cycle derivation is not the finite-$N$ normalization, which is already fixed by \eqref{eq:general-lambda-external-factor-main}, but the marked fixed-cover weight for a general active profile. For NS--NS states this can be derived directly on the covering sphere without first packaging the constituent strings into one compactified puncture operator at each target tube.

On the orbifold side, let
\begin{equation}\label{eq:decorated-class-operator}
\widehat{\mc O}_{[\lambda],\vec\chi}
:=
\frac{1}{\sqrt{|[\lambda,\vec\chi]|_N}}
\sum_{g\in [\lambda,\vec\chi]}
\mc O_{g,\vec\chi}
\end{equation}
denote the normalized decorated class operator with active profile $\lambda=(w_1,\dots,w_{\ell(\lambda)})$ and constituent seed labels $\vec\chi=(\chi_1,\dots,\chi_{\ell(\lambda)})$. Here $[\lambda,\vec\chi]$ is the finite-$N$ orbit of the decorated constituent data under $S_N$, and its size is
\begin{equation}\label{eq:decorated-class-size-main}
|[\lambda,\vec\chi]|_N
=
\frac{N!}{
(N-|\lambda|)!\,
\left(\prod_{a=1}^{\ell(\lambda)} w_a\right)\,
|G_{\lambda,\vec\chi}|
},
\end{equation}
with $G_{\lambda,\vec\chi}$ the subgroup that permutes genuinely identical pairs $(w_a,\chi_a)$. The standard covering-space formula quoted from the symmetric-orbifold literature then takes the form
\begin{equation}\label{eq:general-orbifold-three-point-main}
\begin{aligned}
\mc C_{123}^{\rm orb,(0)}(N;\lambda_i,\vec\chi_i)
&:=
\left\langle
\widehat{\mc O}_{[\lambda_1],\vec\chi_1}(0)\,
\widehat{\mc O}_{[\lambda_2],\vec\chi_2}(1)\,
\widehat{\mc O}_{[\lambda_3],\vec\chi_3}(\infty)
\right\rangle^{\rm conn}_{g=0}
\\
&=
\frac{N!}{(N-d_0)!}\,
\prod_{i=1}^3 \frac{1}{\sqrt{|[\lambda_i,\vec\chi_i]|_N}}\,
\sum_{[f]\in \mathrm{Hurwitz}_0(d_0;\lambda_1,\lambda_2,\lambda_3)}
\frac{\mc C_\perp[f;\lambda_i,\vec\chi_i]}{|\mathrm{Aut}(f)|},
\end{aligned}
\end{equation}
where $d_0=d_0(\lambda_1,\lambda_2,\lambda_3)$ is given by \eqref{eq:general-lambda-degree-main}, and $\mc C_\perp[f;\lambda_i,\vec\chi_i]$ is the reduced free-seed correlator on the covering sphere with constituent insertions at the preimages of the three target punctures. As in the single-cycle case, \eqref{eq:general-orbifold-three-point-main} is quoted orbifold input rather than a derivation performed in this note.

Now fix one connected cover class
\[
[f]\in \mathrm{Hurwitz}_0(d_0;\lambda_1,\lambda_2,\lambda_3),
\]
and for each constituent label $(i,a)$ let $x_{i,a}\in \Sigma\simeq S^2$ be the corresponding preimage of the target puncture $z_i$, so that locally
\[
u-z_i=t_{i,a}^{\,w_{i,a}}
\]
near $x_{i,a}$. It is convenient to abbreviate the full constituent index set by
\begin{equation}\label{eq:constituent-index-set}
\mathcal I:=\{(i,a)\mid i=1,2,3,\ \ a=1,\dots,\ell_i\}.
\end{equation}
For each $\alpha=(i,a)\in \mathcal I$, define the constituent NS--NS representatives on the cover by
\begin{equation}\label{eq:general-cover-constituent-vertices}
\mc V_{\alpha}^{(-1,-1)}
:=
\mc V_{w_{i,a},\chi_{i,a}}^{(-1,-1)}(x_{i,a},\bar x_{i,a}),
\qquad
\mc V_{\alpha}^{(0,0)}
:=
\mc V_{w_{i,a},\chi_{i,a}}^{(0,0)}(x_{i,a},\bar x_{i,a}).
\end{equation}
Choose two distinct labels $\alpha_-,\beta_-\in \mathcal I$ and put all remaining constituent insertions in the $(0,0)$ picture. The original three-tube amplitude still carries the same universal sphere $bc$-ghost factor $\mc N_{\rm sph}^{\rm gh}=1$; the sewn-cover expression below is only a rewriting of the matter and superghost part on the fixed cover. The marked fixed-cover weight is therefore represented by
\begin{equation}\label{eq:general-sewn-cover-weight}
\mc W_f^{\rm mark}(\lambda_i,\vec\chi_i)
:=
\frac{1}{|\mathrm{Aut}(f)|}\,
\Big\langle
\mc V_{\alpha_-}^{(-1,-1)}\,
\mc V_{\beta_-}^{(-1,-1)}\,
\prod_{\gamma\in\mathcal I\setminus\{\alpha_-,\beta_-\}}
\mc V_{\gamma}^{(0,0)}
\Big\rangle_{\Sigma=S^2,f}.
\end{equation}
Because each constituent representative is BRST closed by the single-string calculation of \eqref{eq:single-string-brst-class} and \eqref{eq:longitudinal-zero-picture}, changing which two labels are kept in the $(-1,-1)$ picture changes \eqref{eq:general-sewn-cover-weight} only by a BRST-exact term. Here one must distinguish carefully between the original three-point amplitude on the target sphere and its sewn-cover rewriting. Equation \eqref{eq:general-sewn-cover-weight} is \emph{not} an independent $|\mathcal I|$-point string amplitude on the cover; the points $x_{i,a}$ are fixed algebraic functions of the chosen cover $f$, so there is no new bosonic moduli integral and no new $bc$-ghost zero-mode problem attached to the constituent punctures. The only picture-changing issue is therefore the standard one already present in the original three-point amplitude, and the BRST-exact variation has no moduli boundary term to hit. Thus \eqref{eq:general-sewn-cover-weight} is independent of the constituent picture assignment.

The longitudinal part of \eqref{eq:general-sewn-cover-weight} is the sewn-cover version of the single-cycle Poisson/BF correlator:
\begin{equation}\label{eq:general-psm-cover-factor}
\mc C_f^{\rm PSM}(\lambda_1,\lambda_2,\lambda_3)
:=
\int_{\mathfrak s=f}
\mc D\mathbf X^\pm\,\mc D\mathbf B\,\mc D\bar{\mathbf B}\,
e^{-S_{\rm BF}^{C_{0,3}}[\mathbf X^\pm,\mathbf B,\bar{\mathbf B}]}\,
\prod_{i=1}^3\prod_{a=1}^{\ell_i}
\Sigma^{\rm long}_{w_{i,a};f}(x_{i,a},\bar x_{i,a}).
\end{equation}
The localization argument of \eqref{eq:fixed-cover-psm-localization} applies separately at each preimage $x_{i,a}$. The only singular longitudinal OPEs are the local single-string OPEs already displayed in \eqref{eq:tube-winding-ope} and \eqref{eq:longitudinal-superpartner}: for the lowest state, $\Pi_{\xi_i}(t)\Sigma^{\rm long}_{w_{j,b}}(x_{j,b},\bar x_{j,b})$ is regular away from $t=x_{j,b}$, while $\Pi\Pi$, $\rho\rho$, and mixed $\Pi\rho$ OPEs are regular between distinct constituent insertions. Since the target punctures are distinct and the constituent preimages $x_{i,a}$ are pairwise distinct on the covering sphere for an admissible branch profile, the longitudinal correlator has no singular contraction linking different constituents. Thus the sewn-cover longitudinal path integral factorizes into a product of the same local puncture problems already solved in the single-cycle case. The strict Poisson/BF action still vanishes on the localized cover, and the longitudinal superdeterminant cancellation \eqref{eq:psm-superdet-cancellation} is unchanged. Therefore the constituent cylinder normalizations multiply independently:
\begin{equation}\label{eq:general-psm-cover-independence}
\mc C_f^{\rm PSM}(\lambda_1,\lambda_2,\lambda_3)
=
\prod_{i=1}^3 \prod_{a=1}^{\ell_i} \mc N_{w_{i,a}}
=
\prod_{i=1}^3 \prod_{a=1}^{\ell_i} \sqrt{w_{i,a}}.
\end{equation}
If some constituents are in the $(0,0)$ picture, picture changing can only replace the local bottom component $\Sigma^{\rm long}_{w_{i,a}}$ by the local superpartner $\Theta^{\rm long}_{w_{i,a}}=-w_{i,a}\rho\,\Sigma^{\rm long}_{w_{i,a}}$, so no new cover-dependent interaction between different constituents is introduced in the longitudinal sector.

The remaining cover dependence is exactly the free transverse-seed correlator on the covering sphere,
\begin{equation}\label{eq:general-cover-transverse-factor}
\mc C_\perp[f;\lambda_i,\vec\chi_i],
\end{equation}
defined by the constituent one-copy seed operators and their standard picture-changed descendants at the points $x_{i,a}$. This is the same reduced cover correlator that appears in the orbifold formula \eqref{eq:general-orbifold-three-point-main}. Combining it with \eqref{eq:general-psm-cover-independence} gives
\begin{equation}\label{eq:general-cover-weight-factorization-main}
\mc W_f^{\rm mark}(\lambda_i,\vec\chi_i)
=
\frac{1}{|\mathrm{Aut}(f)|}\,
\left(
\prod_{i=1}^3 \prod_{a=1}^{\ell_i} \sqrt{w_{i,a}}
\right)
\mc C_\perp[f;\lambda_i,\vec\chi_i].
\end{equation}

The physical finite-$N$ string amplitude is therefore
\begin{equation}\label{eq:general-string-three-point-main}
\mc A_{123}^{\rm str,(0)}(N;\lambda_i,\vec\chi_i)
:=
\mc G_N^{\rm ext}(\lambda_1,\vec\chi_1;\lambda_2,\vec\chi_2;\lambda_3,\vec\chi_3)
\sum_{[f]\in \mathrm{Hurwitz}_0(d_0;\lambda_1,\lambda_2,\lambda_3)}
\mc W_f^{\rm mark}(\lambda_i,\vec\chi_i).
\end{equation}
Substituting \eqref{eq:general-cover-weight-factorization-main} and then using the class-normalization identity implied by \eqref{eq:general-lambda-external-factor-main} and \eqref{eq:decorated-class-size-main}, one obtains
\begin{equation}\label{eq:general-string-orbifold-match}
\begin{aligned}
\mc A_{123}^{\rm str,(0)}(N;\lambda_i,\vec\chi_i)
&=
\frac{N!}{(N-d_0)!}\,
\prod_{i=1}^3 \frac{1}{\sqrt{|[\lambda_i,\vec\chi_i]|_N}}\,
\sum_{[f]\in \mathrm{Hurwitz}_0(d_0;\lambda_1,\lambda_2,\lambda_3)}
\frac{\mc C_\perp[f;\lambda_i,\vec\chi_i]}{|\mathrm{Aut}(f)|}
\\
&=
\mc C_{123}^{\rm orb,(0)}(N;\lambda_i,\vec\chi_i).
\end{aligned}
\end{equation}
Thus the strict Poisson/BF worldsheet now reproduces the exact orbifold genus-zero three-point coefficient for arbitrary NS--NS active profiles on $C_{0,3}$, not only for the single-cycle specialization $\lambda_i=(w_i)$. What is still missing is only the more compact puncture-level packaging of this sewn-cover derivation into one explicit local multi-string vertex at each target tube.

Two concrete examples make the general formula less abstract.

First take
\begin{equation}\label{eq:mixed-profile-example-data}
\lambda_1=(2,1),
\qquad
\lambda_2=(2),
\qquad
\lambda_3=(3),
\end{equation}
with distinct constituent seed labels, so every $G_{\lambda_i,\vec\chi_i}$ is trivial. Equation \eqref{eq:general-lambda-degree-main} gives $d_0=3$. One admissible transitive monodromy triple on the active sheet set $\{1,2,3\}$ is
\begin{equation}\label{eq:mixed-profile-example-monodromy}
h_1=(23),
\qquad
h_2=(12),
\qquad
h_3=(132),
\qquad
h_1h_2h_3=1.
\end{equation}
The string-side prefactor from \eqref{eq:general-lambda-external-factor-main} and \eqref{eq:general-cover-weight-factorization-main} is then
\begin{equation}\label{eq:mixed-profile-example-string-factor}
\mc G_N^{\rm ext}\prod_{i,a}\sqrt{w_{i,a}}
=
\frac{(N)_3}{\sqrt{(N)_3(N)_2(N)_3}}\,
\sqrt{2\cdot 1\cdot 2\cdot 3}
=
\frac{2\sqrt{3}}{\sqrt{N(N-1)}}.
\end{equation}
On the orbifold side,
\[
|[(2,1),\vec\chi_1]|_N=\frac{N!}{2(N-3)!},
\qquad
|[(2),\vec\chi_2]|_N=\frac{N!}{2(N-2)!},
\qquad
|[(3),\vec\chi_3]|_N=\frac{N!}{3(N-3)!},
\]
so the class-normalized prefactor in \eqref{eq:general-orbifold-three-point-main} is
\begin{equation}\label{eq:mixed-profile-example-orbifold-factor}
\frac{N!}{(N-3)!}\,
\prod_{i=1}^3 \frac{1}{\sqrt{|[\lambda_i,\vec\chi_i]|_N}}
=
\frac{2\sqrt{3}}{\sqrt{N(N-1)}}.
\end{equation}
Thus the first nontrivial mixed profile, including one active winding-one constituent, matches exactly at the level of the full three-point prefactor before the cover sum is even evaluated.

Second, take a repeated-constituent example
\begin{equation}\label{eq:repeated-profile-example-data}
\lambda_1=(2,2),
\qquad
\lambda_2=(3),
\qquad
\lambda_3=(3),
\end{equation}
for which \eqref{eq:general-lambda-degree-main} gives $d_0=4$. An admissible transitive triple on $\{1,2,3,4\}$ is
\begin{equation}\label{eq:repeated-profile-example-monodromy}
h_1=(12)(34),
\qquad
h_2=(234),
\qquad
h_3=(142),
\qquad
h_1h_2h_3=1.
\end{equation}
If the two winding-two constituents on the first tube carry identical seed data, then $|G_{\lambda_1,\vec\chi_1}|=2!$ and
\begin{equation}\label{eq:repeated-profile-identical-factor}
\mc G_N^{\rm ext}\prod_{i,a}\sqrt{w_{i,a}}
=
\frac{(N)_4\sqrt{2!}}{\sqrt{(N)_4(N)_3(N)_3}}\,
\sqrt{2\cdot 2\cdot 3\cdot 3}
=
6\sqrt{\frac{2(N-3)}{N(N-1)(N-2)}}.
\end{equation}
The same coefficient follows from the decorated class sizes
\[
|[(2,2),(\chi,\chi)]|_N=\frac{N!}{8(N-4)!},
\qquad
|[(3),\vec\chi_2]|_N=|[(3),\vec\chi_3]|_N=\frac{N!}{3(N-3)!}.
\]
If instead the two winding-two constituents carry distinct seed labels, then $|G_{\lambda_1,\vec\chi_1}|=1$ and the coefficient drops by the expected factor $1/\sqrt{2!}$:
\begin{equation}\label{eq:repeated-profile-distinct-factor}
\mc G_N^{\rm ext}\prod_{i,a}\sqrt{w_{i,a}}
=
6\sqrt{\frac{N-3}{N(N-1)(N-2)}}.
\end{equation}
So the quotient by identical-particle symmetry is visible directly in the full three-point amplitude, not only in the separate state-normalization note.

The status is therefore now sharper than in the earlier draft. Established here are the explicit local longitudinal ramification operator \eqref{eq:fixed-cover-vertex-factorization}, the local superconformal OPEs \eqref{eq:longitudinal-primary-ope}--\eqref{eq:full-matter-superprimary-ope}, the BRST-closure calculation \eqref{eq:single-string-brst-class} for the lowest $(-1,-1)$ NS--NS sphere representative, the induced BRST-closed $0$-picture representative \eqref{eq:longitudinal-zero-picture}, the non-exactness argument from the cylinder pairing \eqref{eq:nonexact-cylinder-pairing}, the localization of the strict Poisson/BF path integral onto branched covers, the vanishing of the localized classical BF action, the cancellation of the longitudinal nonzero-mode superdeterminant imported from the companion BRST analysis, the local normalization $\mc N_w=\sqrt w$, and the resulting sphere amplitude \eqref{eq:tree-level-hurwitz-reduction}. The separate notes \texttt{ASYMPTOTIC\_STATE\_MAP.tex} and \texttt{ASYMPTOTIC\_STATE\_MAP\_GENERAL\_LAMBDA.tex} derive the exact finite-$N$ external factors for the lowest single-cycle sector and for general NS--NS profiles, while the sewn-cover derivation \eqref{eq:general-string-orbifold-match} upgrades that normalization data to a full genus-zero orbifold match for arbitrary NS--NS active profiles on $C_{0,3}$. What remains open is no longer the existence of the lowest NS--NS sphere class itself, nor the exact finite-$N$ normalization of that lowest single-cycle sphere amplitude, nor the NS--NS state-map combinatorics for general $\lambda_i$, nor the NS--NS genus-zero three-point amplitude on $C_{0,3}$. The open problems are instead the compactified BRST-complete local vertex for general profiles $\lambda_i$, the extension to Ramond external states, higher-genus and higher-point amplitudes, and the full nonchiral quantum completion of the finite-$\Aeff$ deformation on general curved targets.

\section{Immediate Checks}
The next steps seem concrete.
\begin{itemize}
\item Package the sewn-cover construction \eqref{eq:general-sewn-cover-weight} into one compactified BRST-complete local puncture operator for each general profile $\lambda_i$, and then extend that operator construction to Ramond external states.
\item Generalize the sewn-cover NS--NS derivation from the three-punctured sphere to higher-point amplitudes, where the cover data acquire genuine moduli and the localization measure is less rigid.
\item Extend the genus-one check above from the thermal torus to more general background Riemann surfaces and identify what replaces the long-cycle projector.
\item Clarify how the exact Weyl-structure independence of the Poisson/BF core survives the full nonchiral quantum completion on curved $C$, keeping separate the distinct problem of the finite-$\Aeff$ benchmark deformation.
\end{itemize}

In short, the point of departure is simple. Start from the exact first-order string of \cite{gomis2000nonrelativisticclosedstringtheory}, keep the eight free transverse multiplets, and regard the longitudinal pair $(X^+,X^-)$ as coordinates on a genuine target Riemann surface. Nekrasov's curved $\beta\gamma$ framework \cite{nekrasov2005curvedbetagammasystems} is the essential tool for making this coordinate transformation problem globally well defined, while the companion BRST analysis shows that the full super longitudinal multiplet has a global BRST current on a target curve. What is derived here is the classical patching structure, the orbifold bookkeeping formula \eqref{eq:orbifold-free-energy-log}, the thermal-spin-structure reformulation of the quoted Gomis--Ooguri genus-one result that yields the matching \eqref{eq:degeneracy-match}--\eqref{eq:free-energy-match} for $[\nu_t,\nu_x]=[1,0]$, and an explicit sphere construction not only for the lowest supersymmetric single-cycle states on $C_{0,3}$ but, by sewn-cover factorization, for arbitrary NS--NS active profiles on the same target. The longitudinal ramification operator \eqref{eq:fixed-cover-vertex-factorization} produces the local winding OPE \eqref{eq:tube-winding-ope}; its OPEs with the local matter stress tensor and supercurrent show that the full matter insertion is a weight-$(\tfrac12,\tfrac12)$ NS superprimary, and the bosonized BRST-current calculation \eqref{eq:single-string-brst-class} then proves that the $(-1,-1)$ representative is BRST closed. The cylinder pairing \eqref{eq:nonexact-cylinder-pairing} shows that this class is not BRST exact, while picture changing gives the BRST-closed $0$-picture representative \eqref{eq:longitudinal-zero-picture}. The strict Poisson/BF path integral localizes onto branched covers with vanishing classical BF action \eqref{eq:psm-classical-action-zero}; the longitudinal nonzero-mode determinant cancels as in \eqref{eq:psm-superdet-cancellation}; and cylinder normalization fixes the local factor $\sqrt{w}$ in \eqref{eq:local-normalization-sqrtw}. The separate notes \texttt{ASYMPTOTIC\_STATE\_MAP.tex} and \texttt{ASYMPTOTIC\_STATE\_MAP\_GENERAL\_LAMBDA.tex} then derive the exact finite-$N$ external factors for the lowest single-cycle sector and for general NS--NS active profiles, respectively. As a result, the genus-zero worldsheet amplitude \eqref{eq:tree-level-hurwitz-reduction} reproduces the exact orbifold three-point coefficient with no remaining fitted normalization in the lowest single-cycle sector, while the sewn-cover formula \eqref{eq:general-string-orbifold-match} does the same for arbitrary NS--NS active profiles. What remains conjectural or incomplete is the compactified BRST-complete realization of the general $\lambda_i$ puncture operators, the extension to Ramond external states, the extension to higher-point or higher-genus observables, and the full nonchiral quantum completion on curved $C$. Any deformation toward matrix string theory or full two-dimensional $(8,8)$ SYM would be a separate problem and is not part of the present note.

\printbibliography

\end{document}
